---
title: "MR Inflammation-PD - Tables and figures supplementary"
output:
  word_document:
    fig_caption: TRUE
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  echo = FALSE,
  warning = FALSE,
  message = FALSE
)
```

```{r}
library(tidyverse)
library(MendelianRandomization)
library(TwoSampleMR)
library(knitr)
library(meta)
library(officer)
library(flextable)
library(patchwork)
theme_set(theme_light())

autonum <- run_autonum(post_label = ". ")

# Load the results of the paper ----------------------------------------
load(here::here("all", "paper_results.rda"))
```

# Supplementary files

## Tables

### Harmonized datasets

```{r}
# CRP - PD: r2<0.001 ---------------------------------------------------
bind_rows(
  ligthart_results$pd$primary_r2_0001$data %>% 
    dplyr::mutate(
      source = "Ligthart et al.",
      Position_x = as.character(Position_x)
    ),
  ccgc_results$pd$primary_r2_0001$data %>% 
    dplyr::mutate(
      source = "CCGC",
      Position_x = as.character(Position_x)
    )
) %>% 
  dplyr::select(
    source, SNP, Closest_gene, Chromosome_x, Position_x, A1_x, A2_x,
    freq_x, beta_x, se_x, p_x, beta_y, se_y, p_y
  ) %>% 
  dplyr::mutate(
    across(c(beta_x, se_x, beta_y, se_y), ~ round(.x, 5L)),
    across(c(p_x, p_y), ~ format(.x, scientific = TRUE)),
    freq_x = round(freq_x, 3L)
  ) %>% 
  dplyr::rename(
    `Data source` = source,
    `Closest gene` = Closest_gene, 
    Chromosome = Chromosome_x, 
    `Position (GRCh37)` = Position_x,
    `Effect allele` = A1_x,
    `Reference allele` = A2_x,
    EAF = freq_x,
    `Beta (exposure)` = beta_x,
    `S.E. (exposure)` = se_x,
    `P-value (exposure)` = p_x,
    `Beta (outcome)` = beta_y,
    `S.E. (outcome)` = se_y,
    `P-value (outcome)` = p_y
  ) %>% 
  flextable() %>% 
  autofit() %>% 
  set_caption(
    caption = "Harmonized data for CRP and Parkinson's disease with
    r2<0.001",
    autonum = autonum
  )
```

```{r}
# CRP - PD: r2<0.1 -----------------------------------------------------
bind_rows(
  ligthart_results$pd$primary_r2_01$data %>% 
    dplyr::mutate(
      source = "Ligthart et al.",
      Position_x = as.character(Position_x)
    ),
  ccgc_results$pd$primary_r2_01$data %>% 
    dplyr::mutate(
      source = "CCGC",
      Position_x = as.character(Position_x)
    )
) %>% 
  dplyr::select(
    source, SNP, Closest_gene, Chromosome_x, Position_x, A1_x, A2_x,
    freq_x, beta_x, se_x, p_x, beta_y, se_y, p_y
  ) %>% 
  dplyr::mutate(
    across(c(beta_x, se_x, beta_y, se_y), ~ round(.x, 5L)),
    across(c(p_x, p_y), ~ format(.x, scientific = TRUE)),
    freq_x = round(freq_x, 3L)
  ) %>% 
  dplyr::rename(
    `Data source` = source,
    `Closest gene` = Closest_gene, 
    Chromosome = Chromosome_x, 
    `Position (GRCh37)` = Position_x,
    `Effect allele` = A1_x,
    `Reference allele` = A2_x,
    EAF = freq_x,
    `Beta (exposure)` = beta_x,
    `S.E. (exposure)` = se_x,
    `P-value (exposure)` = p_x,
    `Beta (outcome)` = beta_y,
    `S.E. (outcome)` = se_y,
    `P-value (outcome)` = p_y
  ) %>% 
  flextable() %>% 
  autofit() %>% 
  set_caption(
    caption = "Harmonized data for CRP and Parkinson's disease with
    r2<0.1",
    autonum = autonum
  )
```

```{r}
# CRP - AAO: r2<0.001 --------------------------------------------------
bind_rows(
  ligthart_results$aao$primary_r2_0001$data %>% 
    dplyr::mutate(
      source = "Ligthart et al.",
      Position_x = as.character(Position_x)
    ),
  ccgc_results$aao$primary_r2_0001$data %>% 
    dplyr::mutate(
      source = "CCGC",
      Position_x = as.character(Position_x)
    )
) %>% 
  dplyr::select(
    source, SNP, Closest_gene, Chromosome_x, Position_x, A1_x, A2_x,
    freq_x, beta_x, se_x, p_x, beta_y, se_y, p_y
  ) %>% 
  dplyr::mutate(
    across(c(beta_x, se_x, beta_y, se_y), ~ round(.x, 5L)),
    across(c(p_x, p_y), ~ format(.x, scientific = TRUE)),
    freq_x = round(freq_x, 3L)
  ) %>% 
  dplyr::rename(
    `Data source` = source,
    `Closest gene` = Closest_gene, 
    Chromosome = Chromosome_x, 
    `Position (GRCh37)` = Position_x,
    `Effect allele` = A1_x,
    `Reference allele` = A2_x,
    EAF = freq_x,
    `Beta (exposure)` = beta_x,
    `S.E. (exposure)` = se_x,
    `P-value (exposure)` = p_x,
    `Beta (outcome)` = beta_y,
    `S.E. (outcome)` = se_y,
    `P-value (outcome)` = p_y
  ) %>% 
  flextable() %>% 
  autofit() %>% 
  set_caption(
    caption = "Harmonized data for CRP and AAO with r2<0.001",
    autonum = autonum
  )
```

```{r}
# CRP - AAO: r2<0.1 ----------------------------------------------------
bind_rows(
  ligthart_results$aao$primary_r2_01$data %>% 
    dplyr::mutate(
      source = "Ligthart et al.",
      Position_x = as.character(Position_x)
    ),
  ccgc_results$aao$primary_r2_01$data %>% 
    dplyr::mutate(
      source = "CCGC",
      Position_x = as.character(Position_x)
    )
) %>% 
  dplyr::select(
    source, SNP, Closest_gene, Chromosome_x, Position_x, A1_x, A2_x,
    freq_x, beta_x, se_x, p_x, beta_y, se_y, p_y
  ) %>% 
  dplyr::mutate(
    across(c(beta_x, se_x, beta_y, se_y), ~ round(.x, 5L)),
    across(c(p_x, p_y), ~ format(.x, scientific = TRUE)),
    freq_x = round(freq_x, 3L)
  ) %>% 
  dplyr::rename(
    `Data source` = source,
    `Closest gene` = Closest_gene, 
    Chromosome = Chromosome_x, 
    `Position (GRCh37)` = Position_x,
    `Effect allele` = A1_x,
    `Reference allele` = A2_x,
    EAF = freq_x,
    `Beta (exposure)` = beta_x,
    `S.E. (exposure)` = se_x,
    `P-value (exposure)` = p_x,
    `Beta (outcome)` = beta_y,
    `S.E. (outcome)` = se_y,
    `P-value (outcome)` = p_y
  ) %>% 
  flextable() %>% 
  autofit() %>% 
  set_caption(
    caption = "Harmonized data for CRP and AAO with r2<0.1",
    autonum = autonum
  )
```

```{r}
# IL6 - PD: r2<0.001 ---------------------------------------------------
bind_rows(
  ahluwalia_results$pd$primary_r2_0001$data %>% 
    mutate(
      source = "Ahluwalia et al.",
      Position_x = as.character(Position_x)
    ),
  il6r_results$pd$primary$data %>% 
    mutate(
      source = "IL6R Genetic Consortium", 
      Position_x = as.character(Position_x)
    ),
  folkersen_results$pd$primary_r2_0001$data %>% 
    mutate(
      source = "Folkersen et al. IL-6",
      Position_x = as.character(Position_x)
    )
) %>% 
  dplyr::select(
    source, SNP, Gene, Chromosome_x, Position_x, A1_x, A2_x,
    freq_x, beta_x, se_x, p_x, beta_y, se_y, p_y
  ) %>% 
  dplyr::mutate(
    across(c(beta_x, se_x, beta_y, se_y), ~ round(.x, 5L)),
    across(c(p_x, p_y), ~ format(.x, scientific = TRUE)),
    freq_x = round(freq_x, 3L)
  ) %>% 
  dplyr::rename(
    `Data source` = source,
    `Closest gene` = Gene, 
    Chromosome = Chromosome_x, 
    `Position (GRCh37)` = Position_x,
    `Effect allele` = A1_x,
    `Reference allele` = A2_x,
    EAF = freq_x,
    `Beta (exposure)` = beta_x,
    `S.E. (exposure)` = se_x,
    `P-value (exposure)` = p_x,
    `Beta (outcome)` = beta_y,
    `S.E. (outcome)` = se_y,
    `P-value (outcome)` = p_y
  ) %>% 
  flextable() %>% 
  autofit() %>% 
  set_caption(
    caption = "Harmonized data for IL-6 and Parkinson's disease with
    r2<0.001",
    autonum = autonum
  )
```

```{r}
# IL6 - PD: r2<0.01 ----------------------------------------------------
bind_rows(
  ahluwalia_results$pd$primary_r2_01$data %>% 
    mutate(
      source = "Ahluwalia et al.",
      Position_x = as.character(Position_x)
    ),
  folkersen_results$pd$primary_r2_01$data %>% 
    mutate(
      source = "Folkersen et al. IL-6",
      Position_x = as.character(Position_x)
    )
) %>% 
  dplyr::select(
    source, SNP, Gene, Chromosome_x, Position_x, A1_x, A2_x,
    freq_x, beta_x, se_x, p_x, beta_y, se_y, p_y
  ) %>% 
  dplyr::mutate(
    across(c(beta_x, se_x, beta_y, se_y), ~ round(.x, 5L)),
    across(c(p_x, p_y), ~ format(.x, scientific = TRUE)),
    freq_x = round(freq_x, 3L)
  ) %>% 
  dplyr::rename(
    `Data source` = source,
    `Closest gene` = Gene, 
    Chromosome = Chromosome_x, 
    `Position (GRCh37)` = Position_x,
    `Effect allele` = A1_x,
    `Reference allele` = A2_x,
    EAF = freq_x,
    `Beta (exposure)` = beta_x,
    `S.E. (exposure)` = se_x,
    `P-value (exposure)` = p_x,
    `Beta (outcome)` = beta_y,
    `S.E. (outcome)` = se_y,
    `P-value (outcome)` = p_y
  ) %>% 
  flextable() %>% 
  autofit() %>% 
  set_caption(
    caption = "Harmonized data for IL-6 and Parkinson's disease with
    r2<0.1",
    autonum = autonum
  )
```

```{r}
# IL-6 - AAO: r2<0.001 -------------------------------------------------
bind_rows(
  ahluwalia_results$aao$primary_r2_0001$data %>% 
    mutate(
      source = "Ahluwalia et al.",
      Position_x = as.character(Position_x)
    ),
  il6r_results$aao$primary$data %>% 
    mutate(
      source = "IL6R Genetic Consortium", 
      Position_x = as.character(Position_x)
    ),
  folkersen_results$aao$primary_r2_0001$data %>% 
    mutate(
      source = "Folkersen et al. IL-6",
      Position_x = as.character(Position_x)
    )
) %>% 
  dplyr::select(
    source, SNP, Gene, Chromosome_x, Position_x, A1_x, A2_x,
    freq_x, beta_x, se_x, p_x, beta_y, se_y, p_y
  ) %>% 
  dplyr::mutate(
    across(c(beta_x, se_x, beta_y, se_y), ~ round(.x, 5L)),
    across(c(p_x, p_y), ~ format(.x, scientific = TRUE)),
    freq_x = round(freq_x, 3L)
  ) %>% 
  dplyr::rename(
    `Data source` = source,
    `Closestgene` = Gene, 
    Chromosome = Chromosome_x, 
    `Position (GRCh37)` = Position_x,
    `Effect allele` = A1_x,
    `Reference allele` = A2_x,
    EAF = freq_x,
    `Beta (exposure)` = beta_x,
    `S.E. (exposure)` = se_x,
    `P-value (exposure)` = p_x,
    `Beta (outcome)` = beta_y,
    `S.E. (outcome)` = se_y,
    `P-value (outcome)` = p_y
  ) %>% 
  flextable() %>% 
  autofit() %>% 
  set_caption(
    caption = "Harmonized data for IL-6 and AAO with r2<0.001",
    autonum = autonum
  )
```

```{r}
# IL-6 - AAO: r2<0.001 -------------------------------------------------
bind_rows(
  ahluwalia_results$aao$primary_r2_01$data %>% 
    mutate(
      source = "Ahluwalia et al.",
      Position_x = as.character(Position_x)
    ),
  folkersen_results$aao$primary_r2_01$data %>% 
    mutate(
      source = "Folkersen et al. IL-6",
      Position_x = as.character(Position_x)
    )
) %>% 
  dplyr::select(
    source, SNP, Gene, Chromosome_x, Position_x, A1_x, A2_x,
    freq_x, beta_x, se_x, p_x, beta_y, se_y, p_y
  ) %>% 
  dplyr::mutate(
    across(c(beta_x, se_x, beta_y, se_y), ~ round(.x, 5L)),
    across(c(p_x, p_y), ~ format(.x, scientific = TRUE)),
    freq_x = round(freq_x, 3L)
  ) %>% 
  dplyr::rename(
    `Data source` = source,
    `Closestgene` = Gene, 
    Chromosome = Chromosome_x, 
    `Position (GRCh37)` = Position_x,
    `Effect allele` = A1_x,
    `Reference allele` = A2_x,
    EAF = freq_x,
    `Beta (exposure)` = beta_x,
    `S.E. (exposure)` = se_x,
    `P-value (exposure)` = p_x,
    `Beta (outcome)` = beta_y,
    `S.E. (outcome)` = se_y,
    `P-value (outcome)` = p_y
  ) %>% 
  flextable() %>% 
  autofit() %>% 
  set_caption(
    caption = "Harmonized data for IL-6 and AAO with r2<0.1",
    autonum = autonum
  )
```

```{r}
# IL-1ra - PD: r2<0.001 ------------------------------------------------
bind_rows(
  il1ra_results$pd$primary_r2_0001$data %>% 
    dplyr::mutate(
      source = "Folkersen et al. IL-1ra",
      Position_x = as.character(Position_x)
    ),
  herder_results$pd$primary$data %>% 
    dplyr::mutate(
      source = "Herder et al.",
      Position_x = as.character(Position_x)
    )
) %>% 
  dplyr::select(
    source, SNP, Closest_gene, Chromosome_x, Position_x, A1_x, A2_x,
    freq_x, beta_x, se_x, p_x, beta_y, se_y, p_y
  ) %>% 
  dplyr::mutate(
    across(c(beta_x, se_x, beta_y, se_y), ~ round(.x, 5L)),
    across(c(p_x, p_y), ~ format(.x, scientific = TRUE)),
    freq_x = round(freq_x, 3L)
  ) %>% 
  dplyr::rename(
    `Data source` = source,
    `Closest gene` = Closest_gene, 
    Chromosome = Chromosome_x, 
    `Position (GRCh37)` = Position_x,
    `Effect allele` = A1_x,
    `Reference allele` = A2_x,
    EAF = freq_x,
    `Beta (exposure)` = beta_x,
    `S.E. (exposure)` = se_x,
    `P-value (exposure)` = p_x,
    `Beta (outcome)` = beta_y,
    `S.E. (outcome)` = se_y,
    `P-value (outcome)` = p_y
  ) %>% 
  flextable() %>% 
  autofit() %>% 
  set_caption(
    caption = "Harmonized data for IL-1ra and Parkinson's disease with r2<0.001",
    autonum = autonum
  )
```

```{r}
# IL-1ra - PD: r2<0.001 ------------------------------------------------
bind_rows(
  il1ra_results$pd$primary_r2_01$data %>% 
    dplyr::mutate(
      source = "Folkersen et al. IL-1ra",
      Position_x = as.character(Position_x)
    )
) %>% 
  dplyr::select(
    source, SNP, Gene, Chromosome_x, Position_x, A1_x, A2_x,
    freq_x, beta_x, se_x, p_x, beta_y, se_y, p_y
  ) %>% 
  dplyr::mutate(
    across(c(beta_x, se_x, beta_y, se_y), ~ round(.x, 5L)),
    across(c(p_x, p_y), ~ format(.x, scientific = TRUE)),
    freq_x = round(freq_x, 3L)
  ) %>% 
  dplyr::rename(
    `Data source` = source,
    `Closest gene` = Gene, 
    Chromosome = Chromosome_x, 
    `Position (GRCh37)` = Position_x,
    `Effect allele` = A1_x,
    `Reference allele` = A2_x,
    EAF = freq_x,
    `Beta (exposure)` = beta_x,
    `S.E. (exposure)` = se_x,
    `P-value (exposure)` = p_x,
    `Beta (outcome)` = beta_y,
    `S.E. (outcome)` = se_y,
    `P-value (outcome)` = p_y
  ) %>% 
  flextable() %>% 
  autofit() %>% 
  set_caption(
    caption = "Harmonized data for IL-1ra and Parkinson's disease with r2<0.1",
    autonum = autonum
  )
```

```{r}
# IL-1ra - AAO: r2<0.001 -----------------------------------------------
bind_rows(
  il1ra_results$aao$primary_r2_0001$data %>% 
    dplyr::mutate(
      source = "Folkersen et al. IL-1ra",
      Position_x = as.character(Position_x)
    ),
  herder_results$aao$primary$data %>% 
    dplyr::mutate(
      source = "Herder et al.",
      Position_x = as.character(Position_x)
    )
) %>% 
  dplyr::select(
    source, SNP, Gene, Chromosome_x, Position_x, A1_x, A2_x,
    freq_x, beta_x, se_x, p_x, beta_y, se_y, p_y
  ) %>% 
  dplyr::mutate(
    across(c(beta_x, se_x, beta_y, se_y), ~ round(.x, 5L)),
    across(c(p_x, p_y), ~ format(.x, scientific = TRUE)),
    freq_x = round(freq_x, 3L)
  ) %>% 
  dplyr::rename(
    `Data source` = source,
    `Closest gene` = Gene, 
    Chromosome = Chromosome_x, 
    `Position (GRCh37)` = Position_x,
    `Effect allele` = A1_x,
    `Reference allele` = A2_x,
    EAF = freq_x,
    `Beta (exposure)` = beta_x,
    `S.E. (exposure)` = se_x,
    `P-value (exposure)` = p_x,
    `Beta (outcome)` = beta_y,
    `S.E. (outcome)` = se_y,
    `P-value (outcome)` = p_y
  ) %>% 
  flextable() %>% 
  autofit() %>% 
  set_caption(
    caption = "Harmonized data for IL-1ra and AAO with r2<0.001",
    autonum = autonum
  )
```

```{r}
# IL-1ra - AAO: r2<0.1 -------------------------------------------------
bind_rows(
  il1ra_results$aao$primary_r2_01$data %>% 
    dplyr::mutate(
      source = "Folkersen et al. IL-1ra",
      Position_x = as.character(Position_x)
    )
) %>% 
  dplyr::select(
    source, SNP, Gene, Chromosome_x, Position_x, A1_x, A2_x,
    freq_x, beta_x, se_x, p_x, beta_y, se_y, p_y
  ) %>% 
  dplyr::mutate(
    across(c(beta_x, se_x, beta_y, se_y), ~ round(.x, 5L)),
    across(c(p_x, p_y), ~ format(.x, scientific = TRUE)),
    freq_x = round(freq_x, 3L)
  ) %>% 
  dplyr::rename(
    `Data source` = source,
    `Closest gene` = Gene, 
    Chromosome = Chromosome_x, 
    `Position (GRCh37)` = Position_x,
    `Effect allele` = A1_x,
    `Reference allele` = A2_x,
    EAF = freq_x,
    `Beta (exposure)` = beta_x,
    `S.E. (exposure)` = se_x,
    `P-value (exposure)` = p_x,
    `Beta (outcome)` = beta_y,
    `S.E. (outcome)` = se_y,
    `P-value (outcome)` = p_y
  ) %>% 
  flextable() %>% 
  autofit() %>% 
  set_caption(
    caption = "Harmonized data for IL-1ra and AAO with r2<0.1",
    autonum = autonum
  )
```

```{r}
# TNF-alpha - PD: both r2<0.001 and r2<0.1 -----------------------------
tnf_results$pd$primary$data %>% 
  dplyr::mutate(
      source = "Prins et al.",
      Position_x = as.character(Position_x)
    ) %>% 
  dplyr::select(
    source, SNP, Closest_gene, Chromosome_x, Position_x, A1_x, A2_x,
    freq_x, beta_x, se_x, p_x, beta_y, se_y, p_y
  ) %>% 
  dplyr::mutate(
    across(c(beta_x, se_x, beta_y, se_y), ~ round(.x, 5L)),
    across(c(p_x, p_y), ~ format(.x, scientific = TRUE)),
    freq_x = round(freq_x, 3L)
  ) %>% 
  dplyr::rename(
    `Data source` = source,
    `Closest gene` = Closest_gene, 
    Chromosome = Chromosome_x, 
    `Position (GRCh37)` = Position_x,
    `Effect allele` = A1_x,
    `Reference allele` = A2_x,
    EAF = freq_x,
    `Beta (exposure)` = beta_x,
    `S.E. (exposure)` = se_x,
    `P-value (exposure)` = p_x,
    `Beta (outcome)` = beta_y,
    `S.E. (outcome)` = se_y,
    `P-value (outcome)` = p_y
  ) %>% 
  flextable() %>% 
  autofit() %>% 
  set_caption(
    caption = "Harmonized data for TNF-alpha and Parkinson's disease with r2<0.001 and r2<0.1",
    autonum = autonum
  )
```

```{r}
# TNF-alpha - AAO: r2<0.001 and r2<0.1 ---------------------------------
tnf_results$aao$primary$data %>% 
  dplyr::mutate(
      source = "Prins et al.",
      Position_x = as.character(Position_x)
    ) %>% 
  dplyr::select(
    source, SNP, Closest_gene, Chromosome_x, Position_x, A1_x, A2_x,
    freq_x, beta_x, se_x, p_x, beta_y, se_y, p_y
  ) %>% 
  dplyr::mutate(
    across(c(beta_x, se_x, beta_y, se_y), ~ round(.x, 5L)),
    across(c(p_x, p_y), ~ format(.x, scientific = TRUE)),
    freq_x = round(freq_x, 3L)
  ) %>% 
  dplyr::rename(
    `Data source` = source,
    `Closest gene` = Closest_gene, 
    Chromosome = Chromosome_x, 
    `Position (GRCh37)` = Position_x,
    `Effect allele` = A1_x,
    `Reference allele` = A2_x,
    EAF = freq_x,
    `Beta (exposure)` = beta_x,
    `S.E. (exposure)` = se_x,
    `P-value (exposure)` = p_x,
    `Beta (outcome)` = beta_y,
    `S.E. (outcome)` = se_y,
    `P-value (outcome)` = p_y
  ) %>% 
  flextable() %>% 
  autofit() %>% 
  set_caption(
    caption = "Harmonized data for TNF-alpha and AAO with r2<0.001 and r2<0.1",
    autonum = autonum
  )
```

```{r}
# CRP - PD sens: r2<0.001 ----------------------------------------------
ligthart_results$pd$sens_r2_0001$data %>% 
  dplyr::mutate(
    source = "Ligthart et al.",
    Position_x = as.character(Position_x)
  ) %>% 
  dplyr::select(
    source, SNP, Closest_gene, Chromosome_x, Position_x, A1_x, A2_x,
    freq_x, beta_x, se_x, p_x, beta_y, se_y, p_y
  ) %>% 
  dplyr::mutate(
    across(c(beta_x, se_x, beta_y, se_y), ~ round(.x, 5L)),
    across(c(p_x, p_y), ~ format(.x, scientific = TRUE)),
    freq_x = round(freq_x, 3L)
  ) %>% 
  dplyr::rename(
    `Data source` = source,
    `Closest gene` = Closest_gene, 
    Chromosome = Chromosome_x, 
    `Position (GRCh37)` = Position_x,
    `Effect allele` = A1_x,
    `Reference allele` = A2_x,
    EAF = freq_x,
    `Beta (exposure)` = beta_x,
    `S.E. (exposure)` = se_x,
    `P-value (exposure)` = p_x,
    `Beta (outcome)` = beta_y,
    `S.E. (outcome)` = se_y,
    `P-value (outcome)` = p_y
  ) %>% 
  flextable() %>% 
  autofit() %>% 
  set_caption(
    caption = "Sensitivity MR analysis harmonized data for CRP and
    Parkinson's disease with r2<0.001",
    autonum = autonum
  )
```

```{r}
# CRP - PD sens: r2<0.1 ------------------------------------------------
ligthart_results$pd$sens_r2_01$data %>% 
  dplyr::mutate(
    source = "Ligthart et al.",
    Position_x = as.character(Position_x)
  ) %>% 
  dplyr::select(
    source, SNP, Closest_gene, Chromosome_x, Position_x, A1_x, A2_x,
    freq_x, beta_x, se_x, p_x, beta_y, se_y, p_y
  ) %>% 
  dplyr::mutate(
    across(c(beta_x, se_x, beta_y, se_y), ~ round(.x, 5L)),
    across(c(p_x, p_y), ~ format(.x, scientific = TRUE)),
    freq_x = round(freq_x, 3L)
  ) %>% 
  dplyr::rename(
    `Data source` = source,
    `Closest gene` = Closest_gene, 
    Chromosome = Chromosome_x, 
    `Position (GRCh37)` = Position_x,
    `Effect allele` = A1_x,
    `Reference allele` = A2_x,
    EAF = freq_x,
    `Beta (exposure)` = beta_x,
    `S.E. (exposure)` = se_x,
    `P-value (exposure)` = p_x,
    `Beta (outcome)` = beta_y,
    `S.E. (outcome)` = se_y,
    `P-value (outcome)` = p_y
  ) %>% 
  flextable() %>% 
  autofit() %>% 
  set_caption(
    caption = "Sensitivity MR analysis harmonized data for CRP and
    Parkinson's disease with r2<0.1",
    autonum = autonum
  )
```

```{r}
# CRP - AAO sens: r2<0.001 ---------------------------------------------
ligthart_results$aao$sens_r2_0001$data %>% 
  dplyr::mutate(
    source = "Ligthart et al.",
    Position_x = as.character(Position_x)
  ) %>% 
  dplyr::select(
    source, SNP, Closest_gene, Chromosome_x, Position_x, A1_x, A2_x,
    freq_x, beta_x, se_x, p_x, beta_y, se_y, p_y
  ) %>% 
  dplyr::mutate(
    across(c(beta_x, se_x, beta_y, se_y), ~ round(.x, 5L)),
    across(c(p_x, p_y), ~ format(.x, scientific = TRUE)),
    freq_x = round(freq_x, 3L)
  ) %>% 
  dplyr::rename(
    `Data source` = source,
    `Closest gene` = Closest_gene, 
    Chromosome = Chromosome_x, 
    `Position (GRCh37)` = Position_x,
    `Effect allele` = A1_x,
    `Reference allele` = A2_x,
    EAF = freq_x,
    `Beta (exposure)` = beta_x,
    `S.E. (exposure)` = se_x,
    `P-value (exposure)` = p_x,
    `Beta (outcome)` = beta_y,
    `S.E. (outcome)` = se_y,
    `P-value (outcome)` = p_y
  ) %>% 
  flextable() %>% 
  autofit() %>% 
  set_caption(
    caption = "Sensitivity MR analysis harmonized data for CRP and
    AAO with r2<0.001",
    autonum = autonum
  )
```

```{r}
# CRP - AAO sens: r2<0.1 ---------------------------------------------
ligthart_results$aao$sens_r2_01$data %>% 
  dplyr::mutate(
    source = "Ligthart et al.",
    Position_x = as.character(Position_x)
  ) %>% 
  dplyr::select(
    source, SNP, Closest_gene, Chromosome_x, Position_x, A1_x, A2_x,
    freq_x, beta_x, se_x, p_x, beta_y, se_y, p_y
  ) %>% 
  dplyr::mutate(
    across(c(beta_x, se_x, beta_y, se_y), ~ round(.x, 5L)),
    across(c(p_x, p_y), ~ format(.x, scientific = TRUE)),
    freq_x = round(freq_x, 3L)
  ) %>% 
  dplyr::rename(
    `Data source` = source,
    `Closest gene` = Closest_gene, 
    Chromosome = Chromosome_x, 
    `Position (GRCh37)` = Position_x,
    `Effect allele` = A1_x,
    `Reference allele` = A2_x,
    EAF = freq_x,
    `Beta (exposure)` = beta_x,
    `S.E. (exposure)` = se_x,
    `P-value (exposure)` = p_x,
    `Beta (outcome)` = beta_y,
    `S.E. (outcome)` = se_y,
    `P-value (outcome)` = p_y
  ) %>% 
  flextable() %>% 
  autofit() %>% 
  set_caption(
    caption = "Sensitivity MR analysis harmonized data for CRP and
    AAO with r2<0.1",
    autonum = autonum
  )
```

```{r}
# IL6 - PD sensitivity: r2<0.001 ---------------------------------------
bind_rows(
  ahluwalia_results$pd$sens_r2_0001$data %>% 
    mutate(
      source = "Ahluwalia et al.",
      Position_x = as.character(Position_x),
      Closest_gene = "IL6R"
    ),
  folkersen_results$pd$sens_r2_0001$data %>% 
    mutate(
      source = "Folkersen et al.",
      Position_x = as.character(Position_x),
      Closest_gene = "IL6R"
    )
) %>%  
  dplyr::select(
    source, SNP, Gene, Chromosome_x, Position_x, A1_x, A2_x,
    freq_x, beta_x, se_x, p_x, beta_y, se_y, p_y
  ) %>% 
  dplyr::mutate(
    across(c(beta_x, se_x, beta_y, se_y), ~ round(.x, 5L)),
    across(c(p_x, p_y), ~ format(.x, scientific = TRUE)),
    freq_x = round(freq_x, 3L)
  ) %>% 
  dplyr::rename(
    `Data source` = source,
    `Closest gene` = Gene, 
    Chromosome = Chromosome_x, 
    `Position (GRCh37)` = Position_x,
    `Effect allele` = A1_x,
    `Reference allele` = A2_x,
    EAF = freq_x,
    `Beta (exposure)` = beta_x,
    `S.E. (exposure)` = se_x,
    `P-value (exposure)` = p_x,
    `Beta (outcome)` = beta_y,
    `S.E. (outcome)` = se_y,
    `P-value (outcome)` = p_y
  ) %>% 
  flextable() %>% 
  autofit() %>% 
  set_caption(
    caption = "Sensitivity MR analysis harmonized data for IL-6 and 
    Parkinson's disease with r2<0.001",
    autonum = autonum
  )
```

```{r}
# IL6 - PD sensitivity: r2<0.1 -----------------------------------------
bind_rows(
  ahluwalia_results$pd$sens_r2_01$data %>% 
    mutate(
      source = "Ahluwalia et al.",
      Position_x = as.character(Position_x)
    ),
  folkersen_results$pd$sens_r2_01$data %>% 
    mutate(
      source = "Folkersen et al.",
      Position_x = as.character(Position_x)
    )
) %>%  
  dplyr::select(
    source, SNP, Gene, Chromosome_x, Position_x, A1_x, A2_x,
    freq_x, beta_x, se_x, p_x, beta_y, se_y, p_y
  ) %>% 
  dplyr::mutate(
    across(c(beta_x, se_x, beta_y, se_y), ~ round(.x, 5L)),
    across(c(p_x, p_y), ~ format(.x, scientific = TRUE)),
    freq_x = round(freq_x, 3L)
  ) %>% 
  dplyr::rename(
    `Data source` = source,
    `Closest gene` = Gene, 
    Chromosome = Chromosome_x, 
    `Position (GRCh37)` = Position_x,
    `Effect allele` = A1_x,
    `Reference allele` = A2_x,
    EAF = freq_x,
    `Beta (exposure)` = beta_x,
    `S.E. (exposure)` = se_x,
    `P-value (exposure)` = p_x,
    `Beta (outcome)` = beta_y,
    `S.E. (outcome)` = se_y,
    `P-value (outcome)` = p_y
  ) %>% 
  flextable() %>% 
  autofit() %>% 
  set_caption(
    caption = "Sensitivity MR analysis harmonized data for IL-6 and 
    Parkinson's disease with r2<0.1",
    autonum = autonum
  )
```


```{r}
# IL-6 - AAO sensitivity: r2<0.001 -------------------------------------
bind_rows(
  ahluwalia_results$aao$sens_r2_0001$data %>% 
    mutate(
      source = "Ahluwalia et al.",
      Position_x = as.character(Position_x),
      Closest_gene = "IL6R"
    ),
  folkersen_results$aao$sens_r2_0001$data %>% 
    mutate(
      source = "Folkersen et al.",
      Position_x = as.character(Position_x),
      Closest_gene = "IL6R"
    )
) %>%  
  dplyr::select(
    source, SNP, Gene, Chromosome_x, Position_x, A1_x, A2_x,
    freq_x, beta_x, se_x, p_x, beta_y, se_y, p_y
  ) %>% 
  dplyr::mutate(
    across(c(beta_x, se_x, beta_y, se_y), ~ round(.x, 5L)),
    across(c(p_x, p_y), ~ format(.x, scientific = TRUE)),
    freq_x = round(freq_x, 3L)
  ) %>% 
  dplyr::rename(
    `Data source` = source,
    `Closest gene` = Gene, 
    Chromosome = Chromosome_x, 
    `Position (GRCh37)` = Position_x,
    `Effect allele` = A1_x,
    `Reference allele` = A2_x,
    EAF = freq_x,
    `Beta (exposure)` = beta_x,
    `S.E. (exposure)` = se_x,
    `P-value (exposure)` = p_x,
    `Beta (outcome)` = beta_y,
    `S.E. (outcome)` = se_y,
    `P-value (outcome)` = p_y
  ) %>% 
  flextable() %>% 
  autofit() %>% 
  set_caption(
    caption = "Sensitivity MR analysis harmonized data for IL-6 and
    AAO with r2<0.001",
    autonum = autonum
  )
```

```{r}
# IL-6 - AAO sensitivity: r2<0.1 --------------------------------------
bind_rows(
  ahluwalia_results$aao$sens_r2_01$data %>% 
    mutate(
      source = "Ahluwalia et al.",
      Position_x = as.character(Position_x)
    ),
  folkersen_results$aao$sens_r2_01$data %>% 
    mutate(
      source = "Folkersen et al.",
      Position_x = as.character(Position_x)
    )
) %>%  
  dplyr::select(
    source, SNP, Gene, Chromosome_x, Position_x, A1_x, A2_x,
    freq_x, beta_x, se_x, p_x, beta_y, se_y, p_y
  ) %>% 
  dplyr::mutate(
    across(c(beta_x, se_x, beta_y, se_y), ~ round(.x, 5L)),
    across(c(p_x, p_y), ~ format(.x, scientific = TRUE)),
    freq_x = round(freq_x, 3L)
  ) %>% 
  dplyr::rename(
    `Data source` = source,
    `Closest gene` = Gene, 
    Chromosome = Chromosome_x, 
    `Position (GRCh37)` = Position_x,
    `Effect allele` = A1_x,
    `Reference allele` = A2_x,
    EAF = freq_x,
    `Beta (exposure)` = beta_x,
    `S.E. (exposure)` = se_x,
    `P-value (exposure)` = p_x,
    `Beta (outcome)` = beta_y,
    `S.E. (outcome)` = se_y,
    `P-value (outcome)` = p_y
  ) %>% 
  flextable() %>% 
  autofit() %>% 
  set_caption(
    caption = "Sensitivity MR analysis harmonized data for IL-6 and
    AAO with r2<0.1",
    autonum = autonum
  )
```

```{r}
# IL1ra - PD sensitivity: r2<0.001 -------------------------------------
bind_rows(
  il1ra_results$pd$sens_r2_0001$data %>% 
    mutate(
      source = "Folkersen et al.",
      Position_x = as.character(Position_x)
    )
) %>%  
  dplyr::select(
    source, SNP, Gene, Chromosome_x, Position_x, A1_x, A2_x,
    freq_x, beta_x, se_x, p_x, beta_y, se_y, p_y
  ) %>% 
  dplyr::mutate(
    across(c(beta_x, se_x, beta_y, se_y), ~ round(.x, 5L)),
    across(c(p_x, p_y), ~ format(.x, scientific = TRUE)),
    freq_x = round(freq_x, 3L)
  ) %>% 
  dplyr::rename(
    `Data source` = source,
    `Closest gene` = Gene, 
    Chromosome = Chromosome_x, 
    `Position (GRCh37)` = Position_x,
    `Effect allele` = A1_x,
    `Reference allele` = A2_x,
    EAF = freq_x,
    `Beta (exposure)` = beta_x,
    `S.E. (exposure)` = se_x,
    `P-value (exposure)` = p_x,
    `Beta (outcome)` = beta_y,
    `S.E. (outcome)` = se_y,
    `P-value (outcome)` = p_y
  ) %>% 
  flextable() %>% 
  autofit() %>% 
  set_caption(
    caption = "Sensitivity MR analysis harmonized data for IL-1ra and 
    Parkinson's disease with r2<0.001",
    autonum = autonum
  )
```

```{r}
# IL1ra - PD sensitivity: r2<0.1 ---------------------------------------
bind_rows(
  il1ra_results$pd$sens_r2_01$data %>% 
    mutate(
      source = "Folkersen et al.",
      Position_x = as.character(Position_x)
    )
) %>%  
  dplyr::select(
    source, SNP, Gene, Chromosome_x, Position_x, A1_x, A2_x,
    freq_x, beta_x, se_x, p_x, beta_y, se_y, p_y
  ) %>% 
  dplyr::mutate(
    across(c(beta_x, se_x, beta_y, se_y), ~ round(.x, 5L)),
    across(c(p_x, p_y), ~ format(.x, scientific = TRUE)),
    freq_x = round(freq_x, 3L)
  ) %>% 
  dplyr::rename(
    `Data source` = source,
    `Closest gene` = Gene, 
    Chromosome = Chromosome_x, 
    `Position (GRCh37)` = Position_x,
    `Effect allele` = A1_x,
    `Reference allele` = A2_x,
    EAF = freq_x,
    `Beta (exposure)` = beta_x,
    `S.E. (exposure)` = se_x,
    `P-value (exposure)` = p_x,
    `Beta (outcome)` = beta_y,
    `S.E. (outcome)` = se_y,
    `P-value (outcome)` = p_y
  ) %>% 
  flextable() %>% 
  autofit() %>% 
  set_caption(
    caption = "Sensitivity MR analysis harmonized data for IL-1ra and 
    Parkinson's disease with r2<0.1",
    autonum = autonum
  )
```


```{r}
# IL-1ra - AAO sensitivity: r2<0.001 -----------------------------------
bind_rows(
  il1ra_results$aao$sens_r2_0001$data %>% 
    mutate(
      source = "Folkersen et al.",
      Position_x = as.character(Position_x)
    )
) %>%  
  dplyr::select(
    source, SNP, Gene, Chromosome_x, Position_x, A1_x, A2_x,
    freq_x, beta_x, se_x, p_x, beta_y, se_y, p_y
  ) %>% 
  dplyr::mutate(
    across(c(beta_x, se_x, beta_y, se_y), ~ round(.x, 5L)),
    across(c(p_x, p_y), ~ format(.x, scientific = TRUE)),
    freq_x = round(freq_x, 3L)
  ) %>% 
  dplyr::rename(
    `Data source` = source,
    `Closest gene` = Gene, 
    Chromosome = Chromosome_x, 
    `Position (GRCh37)` = Position_x,
    `Effect allele` = A1_x,
    `Reference allele` = A2_x,
    EAF = freq_x,
    `Beta (exposure)` = beta_x,
    `S.E. (exposure)` = se_x,
    `P-value (exposure)` = p_x,
    `Beta (outcome)` = beta_y,
    `S.E. (outcome)` = se_y,
    `P-value (outcome)` = p_y
  ) %>% 
  flextable() %>% 
  autofit() %>% 
  set_caption(
    caption = "Sensitivity MR analysis harmonized data for IL-1ra and
    AAO with r2<0.001",
    autonum = autonum
  )
```

```{r}
# IL-1ra - AAO sensitivity: r2<0.1 -------------------------------------
bind_rows(
  il1ra_results$aao$sens_r2_01$data %>% 
    mutate(
      source = "Folkersen et al.",
      Position_x = as.character(Position_x)
    )
) %>%  
  dplyr::select(
    source, SNP, Gene, Chromosome_x, Position_x, A1_x, A2_x,
    freq_x, beta_x, se_x, p_x, beta_y, se_y, p_y
  ) %>% 
  dplyr::mutate(
    across(c(beta_x, se_x, beta_y, se_y), ~ round(.x, 5L)),
    across(c(p_x, p_y), ~ format(.x, scientific = TRUE)),
    freq_x = round(freq_x, 3L)
  ) %>% 
  dplyr::rename(
    `Data source` = source,
    `Closest gene` = Gene, 
    Chromosome = Chromosome_x, 
    `Position (GRCh37)` = Position_x,
    `Effect allele` = A1_x,
    `Reference allele` = A2_x,
    EAF = freq_x,
    `Beta (exposure)` = beta_x,
    `S.E. (exposure)` = se_x,
    `P-value (exposure)` = p_x,
    `Beta (outcome)` = beta_y,
    `S.E. (outcome)` = se_y,
    `P-value (outcome)` = p_y
  ) %>% 
  flextable() %>% 
  autofit() %>% 
  set_caption(
    caption = "Sensitivity MR analysis harmonized data for IL-6 and
    AAO with r2<0.1",
    autonum = autonum
  )
```

```{r}
# TNF-alpha - PD sensitivity: r2<0.001 and r2<0.1 ----------------------
tnf_results$pd$sens$data %>% 
  dplyr::mutate(
      source = "Prins et al.",
      Position_x = as.character(Position_x)
    ) %>% 
  dplyr::select(
    source, SNP, Closest_gene, Chromosome_x, Position_x, A1_x, A2_x,
    freq_x, beta_x, se_x, p_x, beta_y, se_y, p_y
  ) %>% 
  dplyr::mutate(
    across(c(beta_x, se_x, beta_y, se_y), ~ round(.x, 5L)),
    across(c(p_x, p_y), ~ format(.x, scientific = TRUE)),
    freq_x = round(freq_x, 3L)
  ) %>% 
  dplyr::rename(
    `Data source` = source,
    `Closest gene` = Closest_gene, 
    Chromosome = Chromosome_x, 
    `Position (GRCh37)` = Position_x,
    `Effect allele` = A1_x,
    `Reference allele` = A2_x,
    EAF = freq_x,
    `Beta (exposure)` = beta_x,
    `S.E. (exposure)` = se_x,
    `P-value (exposure)` = p_x,
    `Beta (outcome)` = beta_y,
    `S.E. (outcome)` = se_y,
    `P-value (outcome)` = p_y
  ) %>% 
  flextable() %>% 
  autofit() %>% 
  set_caption(
    caption = "Sensitivity MR analysis harmonized data for TNF-alpha and Parkinson's disease with r2<0.001 and r2<0.1",
    autonum = autonum
  )
```

```{r}
# TNF-alpha - AAO sensitivity: r2<0.001 and r2<0.1 ---------------------
tnf_results$aao$sens$data %>% 
  dplyr::mutate(
      source = "Prins et al.",
      Position_x = as.character(Position_x)
    ) %>% 
  dplyr::select(
    source, SNP, Closest_gene, Chromosome_x, Position_x, A1_x, A2_x,
    freq_x, beta_x, se_x, p_x, beta_y, se_y, p_y
  ) %>% 
  dplyr::mutate(
    across(c(beta_x, se_x, beta_y, se_y), ~ round(.x, 5L)),
    across(c(p_x, p_y), ~ format(.x, scientific = TRUE)),
    freq_x = round(freq_x, 3L)
  ) %>% 
  dplyr::rename(
    `Data source` = source,
    `Closest gene` = Closest_gene, 
    Chromosome = Chromosome_x, 
    `Position (GRCh37)` = Position_x,
    `Effect allele` = A1_x,
    `Reference allele` = A2_x,
    EAF = freq_x,
    `Beta (exposure)` = beta_x,
    `S.E. (exposure)` = se_x,
    `P-value (exposure)` = p_x,
    `Beta (outcome)` = beta_y,
    `S.E. (outcome)` = se_y,
    `P-value (outcome)` = p_y
  ) %>% 
  flextable() %>% 
  autofit() %>% 
  set_caption(
    caption = "Sensitivity MR analysis harmonized data for TNF-alpha and AAO with r2<0.001 and r2<0.1",
    autonum = autonum
  )
```

### Results secondary analyses

```{r}
# PD estimates secondary -----------------------------------------------
pd_secondary_res <- tibble(
  Exposure = c(rep("CRP", 4L), rep("IL-1ra", 4L)),
  `Data source` = c(rep("Ligthart et al.", 4L), rep("Folkersen et al.", 4L)),
  `MR method` = rep(
    c("MR-Egger", "Weighted median", "Weighted mode", "MR-PRESSO"),
    2L
  ),
  est = c(
    ligthart_results$pd$primary_r2_0001$mr_results$egger$estimate$est,
    ligthart_results$pd$primary_r2_0001$mr_results$mr_median$estimate$est,
    ligthart_results$pd$primary_r2_0001$mr_results$mr_mode$estimate$est,
    ligthart_results$pd$primary_r2_0001$mr_results$presso$estimate$est[2],
    il1ra_results$pd$primary_r2_0001$mr_results$egger$estimate$est,
    il1ra_results$pd$primary_r2_0001$mr_results$mr_median$estimate$est,
    il1ra_results$pd$primary_r2_0001$mr_results$mr_mode$estimate$est,
    il1ra_results$pd$primary_r2_0001$mr_results$presso$estimate$est[2]
  ),
  lower = c(
    ligthart_results$pd$primary_r2_0001$mr_results$egger$estimate$lower,
    ligthart_results$pd$primary_r2_0001$mr_results$mr_median$estimate$lower,
    ligthart_results$pd$primary_r2_0001$mr_results$mr_mode$estimate$lower,
    ligthart_results$pd$primary_r2_0001$mr_results$presso$estimate$lower[2],
    il1ra_results$pd$primary_r2_0001$mr_results$egger$estimate$lower,
    il1ra_results$pd$primary_r2_0001$mr_results$mr_median$estimate$lower,
    il1ra_results$pd$primary_r2_0001$mr_results$mr_mode$estimate$lower,
    il1ra_results$pd$primary_r2_0001$mr_results$presso$estimate$lower[2]
  ),
  upper = c(
    ligthart_results$pd$primary_r2_0001$mr_results$egger$estimate$upper,
    ligthart_results$pd$primary_r2_0001$mr_results$mr_median$estimate$upper,
    ligthart_results$pd$primary_r2_0001$mr_results$mr_mode$estimate$upper,
    ligthart_results$pd$primary_r2_0001$mr_results$presso$estimate$upper[2],
    il1ra_results$pd$primary_r2_0001$mr_results$egger$estimate$upper,
    il1ra_results$pd$primary_r2_0001$mr_results$mr_median$estimate$upper,
    il1ra_results$pd$primary_r2_0001$mr_results$mr_mode$estimate$upper,
    il1ra_results$pd$primary_r2_0001$mr_results$presso$estimate$upper[2]
  ),
  pval = c(
    ligthart_results$pd$primary_r2_0001$mr_results$egger$estimate$pval,
    ligthart_results$pd$primary_r2_0001$mr_results$mr_median$estimate$pval,
    ligthart_results$pd$primary_r2_0001$mr_results$mr_mode$estimate$pval,
    ligthart_results$pd$primary_r2_0001$mr_results$presso$estimate$pval[2],
    il1ra_results$pd$primary_r2_0001$mr_results$egger$estimate$pval,
    il1ra_results$pd$primary_r2_0001$mr_results$mr_median$estimate$pval,
    il1ra_results$pd$primary_r2_0001$mr_results$mr_mode$estimate$pval,
    il1ra_results$pd$primary_r2_0001$mr_results$presso$estimate$pval[2]
  )
) %>% 
  mutate(
    across(c(est, lower, upper), ~ round(exp(.x), 3L)),
    outcome = "Parkinson's disease"
  )

# AAO ------------------------------------------------------------------
aao_secondary_res <- tibble(
  Exposure = c(rep("CRP", 4L), rep("IL-1ra", 4L)),
  `Data source` = c(rep("Ligthart et al.", 4L), rep("Folkersen et al.", 4L)),
  `MR method` = rep(
    c("MR-Egger", "Weighted median", "Weighted mode", "MR-PRESSO"),
    2L
  ),
  est = c(
    ligthart_results$aao$primary_r2_0001$mr_results$egger$estimate$est,
    ligthart_results$aao$primary_r2_0001$mr_results$mr_median$estimate$est,
    ligthart_results$aao$primary_r2_0001$mr_results$mr_mode$estimate$est,
    ligthart_results$aao$primary_r2_0001$mr_results$presso$estimate$est[2],
    il1ra_results$aao$primary_r2_0001$mr_results$egger$estimate$est,
    il1ra_results$aao$primary_r2_0001$mr_results$mr_median$estimate$est,
    il1ra_results$aao$primary_r2_0001$mr_results$mr_mode$estimate$est,
    il1ra_results$aao$primary_r2_0001$mr_results$presso$estimate$est[2]
  ),
  lower = c(
    ligthart_results$aao$primary_r2_0001$mr_results$egger$estimate$lower,
    ligthart_results$aao$primary_r2_0001$mr_results$mr_median$estimate$lower,
    ligthart_results$aao$primary_r2_0001$mr_results$mr_mode$estimate$lower,
    ligthart_results$aao$primary_r2_0001$mr_results$presso$estimate$lower[2],
    il1ra_results$aao$primary_r2_0001$mr_results$egger$estimate$lower,
    il1ra_results$aao$primary_r2_0001$mr_results$mr_median$estimate$lower,
    il1ra_results$aao$primary_r2_0001$mr_results$mr_mode$estimate$lower,
    il1ra_results$aao$primary_r2_0001$mr_results$presso$estimate$lower[2]
  ),
  upper = c(
    ligthart_results$aao$primary_r2_0001$mr_results$egger$estimate$upper,
    ligthart_results$aao$primary_r2_0001$mr_results$mr_median$estimate$upper,
    ligthart_results$aao$primary_r2_0001$mr_results$mr_mode$estimate$upper,
    ligthart_results$aao$primary_r2_0001$mr_results$presso$estimate$upper[2],
    il1ra_results$aao$primary_r2_0001$mr_results$egger$estimate$upper,
    il1ra_results$aao$primary_r2_0001$mr_results$mr_median$estimate$upper,
    il1ra_results$aao$primary_r2_0001$mr_results$mr_mode$estimate$upper,
    il1ra_results$aao$primary_r2_0001$mr_results$presso$estimate$upper[2]
  ),
  pval = c(
    ligthart_results$aao$primary_r2_0001$mr_results$egger$estimate$pval,
    ligthart_results$aao$primary_r2_0001$mr_results$mr_median$estimate$pval,
    ligthart_results$aao$primary_r2_0001$mr_results$mr_mode$estimate$pval,
    ligthart_results$aao$primary_r2_0001$mr_results$presso$estimate$pval[2],
    il1ra_results$aao$primary_r2_0001$mr_results$egger$estimate$pval,
    il1ra_results$aao$primary_r2_0001$mr_results$mr_median$estimate$pval,
    il1ra_results$aao$primary_r2_0001$mr_results$mr_mode$estimate$pval,
    il1ra_results$aao$primary_r2_0001$mr_results$presso$estimate$pval[2]
  )
) %>% 
  mutate(outcome = "AAO")
```

```{r}
pd_secondary_res %>% 
  dplyr::select(-outcome) %>% 
  mutate(
    `OR (95% CI)` = glue::glue("{est} ({lower}; {upper})"),
    pval = if_else(
      pval < 0.001, "<0.001",
      as.character(round(pval, 3L))
    )
  ) %>% 
  dplyr::rename(`P-value` = pval) %>% 
  dplyr::select(
    Exposure, `Data source`, `MR method`, `OR (95% CI)`, `P-value`
  ) %>% 
  flextable() %>% 
  autofit() %>% 
  footnote(
    i = 1, j = 4,
    value = as_paragraph(
      "If MR-PRESSO results are set to NA, no outlier was identified and
      the final estimate equals the primary analysis estimate."
    ),
    ref_symbols = "a",
    part = "header", inline = TRUE
  ) %>% 
  set_caption(
    caption = "MR secondary analysis results for PD",
    autonum = autonum
  )
```
 
```{r}
aao_secondary_res %>% 
  dplyr::select(-outcome) %>% 
  mutate(across(c(est, lower, upper), ~ round(.x, 3L))) %>% 
  mutate(
    `Estimate (95% CI)` = glue::glue("{est} ({lower}; {upper})"),
    pval = if_else(
      pval < 0.001, "<0.001",
      as.character(round(pval, 3L))
    )
  ) %>% 
  dplyr::rename(`P-value` = pval) %>% 
  dplyr::select(
    Exposure, `Data source`, `MR method`, `Estimate (95% CI)`, `P-value`
  ) %>% 
  flextable() %>% 
  autofit() %>%
  footnote(
    i = 1, j = 4,
    value = as_paragraph(
      "If MR-PRESSO results are set to NA, no outlier was identified and
      the final estimate equals the primary analysis estimate."
    ),
    ref_symbols = "a",
    part = "header", inline = TRUE
  ) %>% 
  set_caption(
    caption = "MR secondary analysis results for AAO",
    autonum = autonum
  )
```

### Results sensitivity

```{r}
# PD estimates primary sensitivity -----------------------------------
pd_primary_sens <- tibble(
  Exposure = c("CRP", "IL-6", "IL-6", "TNF-alpha"),
  `Data source` = c(
    "Ligthart et al.", "Ahluwalia et al.", "Folkersen et al.", 
    "Prins et al."
  ),
  est = c(
    ligthart_results$pd$sens_r2_0001$mr_results$ivw$estimate$est,
    ahluwalia_results$pd$sens_r2_0001$mr_results@Estimate,
    folkersen_results$pd$sens_r2_0001$mr_results@Estimate,
    tnf_results$pd$sens$mr_results$est
  ),
  lower = c(
    ligthart_results$pd$sens_r2_0001$mr_results$ivw$estimate$lower,
    ahluwalia_results$pd$sens_r2_0001$mr_results@CILower,
    folkersen_results$pd$sens_r2_0001$mr_results@CILower,
    tnf_results$pd$sens$mr_results$lower
  ),
  upper = c(
    ligthart_results$pd$sens_r2_0001$mr_results$ivw$estimate$upper,
    ahluwalia_results$pd$sens_r2_0001$mr_results@CIUpper,
    folkersen_results$pd$sens_r2_0001$mr_results@CIUpper,
    tnf_results$pd$sens$mr_results$upper
  ),
  pval = c(
    ligthart_results$pd$sens_r2_0001$mr_results$ivw$estimate$pval,
    ahluwalia_results$pd$sens_r2_0001$mr_results@Pvalue,
    folkersen_results$pd$sens_r2_0001$mr_results@Pvalue,
    tnf_results$pd$sens$mr_results$pval
  )
) %>% 
  mutate(
    across(c(est, lower, upper), ~ round(exp(.x), 3L)),
    outcome = "Parkinson's disease"
  )

# AAO ------------------------------------------------------------------
aao_primary_sens <- tibble(
  Exposure = c("CRP", "IL-6", "IL-6", "TNF-alpha"),
  `Data source` = c(
    "Ligthart et al.", "Ahluwalia et al.", "Folkersen et al.", 
    "Prins et al."
  ),
  est = c(
    ligthart_results$aao$sens_r2_0001$mr_results$ivw$estimate$est,
    ahluwalia_results$aao$sens_r2_0001$mr_results@Estimate,
    folkersen_results$aao$sens_r2_0001$mr_results@Estimate,
    tnf_results$aao$sens$mr_results$est
  ),
  lower = c(
    ligthart_results$aao$sens_r2_0001$mr_results$ivw$estimate$lower,
    ahluwalia_results$aao$sens_r2_0001$mr_results@CILower,
    folkersen_results$aao$sens_r2_0001$mr_results@CILower,
    tnf_results$aao$sens$mr_results$lower
  ),
  upper = c(
    ligthart_results$aao$sens_r2_0001$mr_results$ivw$estimate$upper,
    ahluwalia_results$aao$sens_r2_0001$mr_results@CIUpper,
    folkersen_results$aao$sens_r2_0001$mr_results@CIUpper,
    tnf_results$aao$sens$mr_results$upper
  ),
  pval = c(
    ligthart_results$aao$sens_r2_0001$mr_results$ivw$estimate$pval,
    ahluwalia_results$aao$sens_r2_0001$mr_results@Pvalue,
    folkersen_results$aao$sens_r2_0001$mr_results@Pvalue,
    tnf_results$aao$sens$mr_results$pval
  )
) %>% 
  mutate(outcome = "AAO")
```

```{r}
pd_primary_sens %>% 
  dplyr::select(-outcome) %>% 
  mutate(
    `OR (95% CI)` = glue::glue("{est} ({lower}; {upper})"),
    pval = if_else(
      pval < 0.001, "<0.001",
      as.character(round(pval, 3L))
    )
  ) %>% 
  dplyr::rename(`P-value` = pval) %>% 
  dplyr::select(
    Exposure, `Data source`, `OR (95% CI)`, `P-value`
  ) %>% 
  flextable() %>% 
  autofit() %>% 
  set_caption(
    caption = "MR primary analysis results on sensitivity for PD",
    autonum = autonum
  )
```
 
```{r}
aao_primary_sens %>% 
  dplyr::select(-outcome) %>% 
  mutate(across(c(est, lower, upper), ~ round(.x, 3L))) %>% 
  mutate(
    `Estimate (95% CI)` = glue::glue("{est} ({lower}; {upper})"),
    pval = if_else(
      pval < 0.001, "<0.001",
      as.character(round(pval, 3L))
    )
  ) %>% 
  dplyr::rename(`P-value` = pval) %>% 
  dplyr::select(
    Exposure, `Data source`, `Estimate (95% CI)`, `P-value`
  ) %>% 
  flextable() %>%
  set_caption(
    caption = "MR primary analysis results on sensitivity for AAO",
    autonum = autonum
  )
```


### Results secondary analyses on sensitivity

```{r}
# PD estimates secondary sensitivity -----------------------------------
pd_secondary_sens <- tibble(
  Exposure = rep("CRP", 4L), 
  `Data source` = rep("Ligthart et al.", 4L),
  `MR method` = c(
    "MR-Egger", "Weighted median", "Weighted mode", "MR-PRESSO"
  ),
  est = c(
    ligthart_results$pd$sens_r2_0001$mr_results$egger$estimate$est,
    ligthart_results$pd$sens_r2_0001$mr_results$mr_median$estimate$est,
    ligthart_results$pd$sens_r2_0001$mr_results$mr_mode$estimate$est,
    ligthart_results$pd$sens_r2_0001$mr_results$presso$estimate$est[2]
  ),
  lower = c(
    ligthart_results$pd$sens_r2_0001$mr_results$egger$estimate$lower,
    ligthart_results$pd$sens_r2_0001$mr_results$mr_median$estimate$lower,
    ligthart_results$pd$sens_r2_0001$mr_results$mr_mode$estimate$lower,
    ligthart_results$pd$sens_r2_0001$mr_results$presso$estimate$lower[2]
  ),
  upper = c(
    ligthart_results$pd$sens_r2_0001$mr_results$egger$estimate$upper,
    ligthart_results$pd$sens_r2_0001$mr_results$mr_median$estimate$upper,
    ligthart_results$pd$sens_r2_0001$mr_results$mr_mode$estimate$upper,
    ligthart_results$pd$sens_r2_0001$mr_results$presso$estimate$upper[2]
  ),
  pval = c(
    ligthart_results$pd$sens_r2_0001$mr_results$egger$estimate$pval,
    ligthart_results$pd$sens_r2_0001$mr_results$mr_median$estimate$pval,
    ligthart_results$pd$sens_r2_0001$mr_results$mr_mode$estimate$pval,
    ligthart_results$pd$sens_r2_0001$mr_results$presso$estimate$pval[2]
  )
) %>% 
  mutate(
    across(c(est, lower, upper), ~ round(exp(.x), 3L)),
    outcome = "Parkinson's disease"
  )

# AAO ------------------------------------------------------------------
aao_secondary_sens <- tibble(
  Exposure = rep("CRP", 4L), 
  `Data source` = rep("Ligthart et al.", 4L),
  `MR method` = c(
    "MR-Egger", "Weighted median", "Weighted mode", "MR-PRESSO"
  ),
  est = c(
    ligthart_results$aao$sens_r2_0001$mr_results$egger$estimate$est,
    ligthart_results$aao$sens_r2_0001$mr_results$mr_median$estimate$est,
    ligthart_results$aao$sens_r2_0001$mr_results$mr_mode$estimate$est,
    ligthart_results$aao$sens_r2_0001$mr_results$presso$estimate$est[2]
  ),
  lower = c(
    ligthart_results$aao$sens_r2_0001$mr_results$egger$estimate$lower,
    ligthart_results$aao$sens_r2_0001$mr_results$mr_median$estimate$lower,
    ligthart_results$aao$sens_r2_0001$mr_results$mr_mode$estimate$lower,
    ligthart_results$aao$sens_r2_0001$mr_results$presso$estimate$lower[2]
  ),
  upper = c(
    ligthart_results$aao$sens_r2_0001$mr_results$egger$estimate$upper,
    ligthart_results$aao$sens_r2_0001$mr_results$mr_median$estimate$upper,
    ligthart_results$aao$sens_r2_0001$mr_results$mr_mode$estimate$upper,
    ligthart_results$aao$sens_r2_0001$mr_results$presso$estimate$upper[2]
  ),
  pval = c(
    ligthart_results$aao$sens_r2_0001$mr_results$egger$estimate$pval,
    ligthart_results$aao$sens_r2_0001$mr_results$mr_median$estimate$pval,
    ligthart_results$aao$sens_r2_0001$mr_results$mr_mode$estimate$pval,
    ligthart_results$aao$sens_r2_0001$mr_results$presso$estimate$pval[2]
  )
) %>% 
  mutate(outcome = "AAO")
```

```{r}
pd_secondary_sens %>% 
  dplyr::select(-outcome) %>% 
  mutate(
    `OR (95% CI)` = glue::glue("{est} ({lower}; {upper})"),
    pval = if_else(
      pval < 0.001, "<0.001",
      as.character(round(pval, 3L))
    )
  ) %>% 
  dplyr::rename(`P-value` = pval) %>% 
  dplyr::select(
    Exposure, `Data source`, `MR method`, `OR (95% CI)`, `P-value`
  ) %>% 
  flextable() %>% 
  footnote(
    i = 1, j = 4,
    value = as_paragraph(
      "If MR-PRESSO results are set to NA, no outlier was identified and
      the final estimate equals the primary analysis estimate."
    ),
    ref_symbols = "a",
    part = "header", inline = TRUE
  ) %>% 
  autofit() %>% 
  set_caption(
    caption = "MR secondary analysis results on sensitivity for PD",
    autonum = autonum
  )
```
 
```{r}
aao_secondary_sens %>% 
  dplyr::select(-outcome) %>% 
  mutate(across(c(est, lower, upper), ~ round(.x, 3L))) %>% 
  mutate(
    `Estimate (95% CI)` = glue::glue("{est} ({lower}; {upper})"),
    pval = if_else(
      pval < 0.001, "<0.001",
      as.character(round(pval, 3L))
    )
  ) %>% 
  dplyr::rename(`P-value` = pval) %>% 
  dplyr::select(
    Exposure, `Data source`, `MR method`, `Estimate (95% CI)`, `P-value`
  ) %>% 
  flextable() %>% 
  footnote(
    i = 1, j = 4,
    value = as_paragraph(
      "If MR-PRESSO results are set to NA, no outlier was identified and
      the final estimate equals the primary analysis estimate."
    ),
    ref_symbols = "a",
    part = "header", inline = TRUE
  )  %>% 
  autofit() %>% 
  set_caption(
    caption = "MR secondary analysis results on sensitivity for AAO",
    autonum = autonum
  )
```

### Description IVs selected with r2<0.1

```{r}
# Describe instruments in each scenario --------------------------------
iv_desc_pd <- bind_rows(
  ligthart_results$pd$primary_r2_0001$statistics,
  ligthart_results$pd$primary_r2_01$statistics,
) |> 
  add_column(
    `N IVs` = c(
      nrow(ligthart_results$pd$primary_r2_0001$data),
      nrow(ligthart_results$pd$primary_r2_01$data)
    ), .before = 1
  ) |> 
  dplyr::select(`N IVs`, f_stat, r2) |> 
  dplyr::rename(`F-statistic` = f_stat, `R2` = r2)

iv_desc_aao <- bind_rows(
  ligthart_results$aao$primary_r2_0001$statistics,
  ligthart_results$aao$primary_r2_01$statistics,
) |> 
  add_column(
    `N IVs` = c(
      nrow(ligthart_results$aao$primary_r2_0001$data),
      nrow(ligthart_results$aao$primary_r2_01$data)
    ), .before = 1
  ) |> 
  dplyr::select(`N IVs`, f_stat, r2) |> 
  dplyr::rename(`F-statistic` = f_stat, `R2` = r2)
```

```{r}
iv_desc_pd |> 
  flextable() %>% 
  autofit()
```

```{r}
iv_desc_aao |> 
  flextable() %>% 
  autofit()
```

```{r}
# Describe instruments in each scenario --------------------------------
iv_desc_pd <- bind_rows(
  tibble(
    SNP = paste(
      ccgc_results$pd$primary_r2_01$mr_results$SNP, collapse = "; "
    ),
    `N IVs` = nrow(ccgc_results$pd$primary_r2_01$mr_results),
    `F-statistic` = paste(
      ccgc_results$pd$primary_r2_01$mr_results$`F-statistic`, 
      collapse = "; "
    ),
    `R^2` = sum(ccgc_results$pd$primary_r2_01$mr_results$`R^2`)
  ),
  ccgc_results$pd$primary_r2_0001$mr_results |> 
    mutate(`N IVs` = 1, `F-statistic` = as.character(`F-statistic`))
)  |> 
  dplyr::select(`N IVs`, `F-statistic`, `R^2`)

iv_desc_aao <- bind_rows(
  tibble(
    SNP = paste(
      ccgc_results$aao$primary_r2_01$mr_results$SNP, collapse = "; "
    ),
    `N IVs` = nrow(ccgc_results$aao$primary_r2_01$mr_results),
    `F-statistic` = paste(
      ccgc_results$aao$primary_r2_01$mr_results$`F-statistic`, 
      collapse = "; "
    ),
    `R^2` = sum(ccgc_results$aao$primary_r2_01$mr_results$`R^2`)
  ),
  ccgc_results$aao$primary_r2_0001$mr_results |> 
    mutate(`N IVs` = 1, `F-statistic` = as.character(`F-statistic`))
)  |> 
  dplyr::select(`N IVs`, `F-statistic`, `R^2`)
```

```{r}
iv_desc_pd |> 
  flextable() %>% 
  autofit()
```

```{r}
iv_desc_aao |> 
  flextable() %>% 
  autofit()
```

```{r}
# Describe instruments in each scenario --------------------------------
iv_desc_pd <- bind_rows(
  ahluwalia_results$pd$primary_r2_0001$statistics,
  ahluwalia_results$pd$primary_r2_01$statistics |> 
    mutate(SNP = as.character(SNP)),
) |> 
  add_column(
    `N IVs` = c(
      nrow(ahluwalia_results$pd$primary_r2_0001$data),
      nrow(ahluwalia_results$pd$primary_r2_01$data)
    ), .before = 1
  ) |> 
  dplyr::select(`N IVs`, f_stat, r2) |> 
  dplyr::rename(`F-statistic` = f_stat, `R2` = r2)

iv_desc_aao <- bind_rows(
  ahluwalia_results$aao$primary_r2_0001$statistics,
  ahluwalia_results$aao$primary_r2_01$statistics |> 
    mutate(SNP = as.character(SNP)),
) |> 
  add_column(
    `N IVs` = c(
      nrow(ahluwalia_results$aao$primary_r2_0001$data),
      nrow(ahluwalia_results$aao$primary_r2_01$data)
    ), .before = 1
  ) |> 
  dplyr::select(`N IVs`, f_stat, r2) |> 
  dplyr::rename(`F-statistic` = f_stat, `R2` = r2)
```

```{r}
iv_desc_pd |> 
  flextable() %>% 
  autofit()
```

```{r}
iv_desc_aao |> 
  flextable() %>% 
  autofit()
```

```{r}
# Describe instruments in each scenario --------------------------------
iv_desc_pd <- bind_rows(
  folkersen_results$pd$primary_r2_0001$statistics,
  folkersen_results$pd$primary_r2_01$statistics |> 
    mutate(SNP = as.character(SNP)),
) |> 
  add_column(
    `N IVs` = c(
      nrow(folkersen_results$pd$primary_r2_0001$data),
      nrow(folkersen_results$pd$primary_r2_01$data)
    ), .before = 1
  ) |> 
  dplyr::select(`N IVs`, f_stat, r2) |> 
  dplyr::rename(`F-statistic` = f_stat, `R2` = r2)

iv_desc_aao <- bind_rows(
  folkersen_results$aao$primary_r2_0001$statistics,
  folkersen_results$aao$primary_r2_01$statistics |> 
    mutate(SNP = as.character(SNP)),
) |> 
  add_column(
    `N IVs` = c(
      nrow(folkersen_results$aao$primary_r2_0001$data),
      nrow(folkersen_results$aao$primary_r2_01$data)
    ), .before = 1
  ) |> 
  dplyr::select(`N IVs`, f_stat, r2) |> 
  dplyr::rename(`F-statistic` = f_stat, `R2` = r2)
```

```{r}
iv_desc_pd |> 
  flextable() %>% 
  autofit()
```

```{r}
iv_desc_aao |> 
  flextable() %>% 
  autofit()
```

```{r}
# Describe instruments in each scenario --------------------------------
iv_desc_pd <- bind_rows(
  il1ra_results$pd$primary_r2_0001$statistics,
  il1ra_results$pd$primary_r2_01$statistics |> 
    mutate(SNP = as.character(SNP)),
) |> 
  add_column(
    `N IVs` = c(
      nrow(il1ra_results$pd$primary_r2_0001$data),
      nrow(il1ra_results$pd$primary_r2_01$data)
    ), .before = 1
  ) |> 
  dplyr::select(`N IVs`, f_stat, r2) |> 
  dplyr::rename(`F-statistic` = f_stat, `R2` = r2)

iv_desc_aao <- bind_rows(
  il1ra_results$aao$primary_r2_0001$statistics,
  il1ra_results$aao$primary_r2_01$statistics |> 
    mutate(SNP = as.character(SNP)),
) |> 
  add_column(
    `N IVs` = c(
      nrow(il1ra_results$aao$primary_r2_0001$data),
      nrow(il1ra_results$aao$primary_r2_01$data)
    ), .before = 1
  ) |> 
  dplyr::select(`N IVs`, f_stat, r2) |> 
  dplyr::rename(`F-statistic` = f_stat, `R2` = r2)
```

```{r}
iv_desc_pd |> 
  flextable() %>% 
  autofit()
```

```{r}
iv_desc_aao |> 
  flextable() %>% 
  autofit()
```

### Results r2<0.1
```{r}
# PD estimates secondary -----------------------------------------------
pd_res <- tibble(
  `MR method` = c(
      "IVW-RE", "MR-Egger", "Weighted median", "Weighted mode", 
      "MR-PRESSO", "IVW-RE-Corr"
  ),
  est = c(
    ligthart_results$pd$primary_r2_01$mr_results$ivw$estimate$est,
    ligthart_results$pd$primary_r2_01$mr_results$egger$estimate$est,
    ligthart_results$pd$primary_r2_01$mr_results$mr_median$estimate$est,
    ligthart_results$pd$primary_r2_01$mr_results$mr_mode$estimate$est,
    ligthart_results$pd$primary_r2_01$mr_results$presso$estimate$est[2],
    ligthart_results$pd$primary_r2_01$mr_results_corr@Estimate
  ),
  lower = c(
    ligthart_results$pd$primary_r2_01$mr_results$ivw$estimate$lower,
    ligthart_results$pd$primary_r2_01$mr_results$egger$estimate$lower,
    ligthart_results$pd$primary_r2_01$mr_results$mr_median$estimate$lower,
    ligthart_results$pd$primary_r2_01$mr_results$mr_mode$estimate$lower,
    ligthart_results$pd$primary_r2_01$mr_results$presso$estimate$lower[2],
    ligthart_results$pd$primary_r2_01$mr_results_corr@CILower
  ),
  upper = c(
    ligthart_results$pd$primary_r2_01$mr_results$ivw$estimate$upper,
    ligthart_results$pd$primary_r2_01$mr_results$egger$estimate$upper,
    ligthart_results$pd$primary_r2_01$mr_results$mr_median$estimate$upper,
    ligthart_results$pd$primary_r2_01$mr_results$mr_mode$estimate$upper,
    ligthart_results$pd$primary_r2_01$mr_results$presso$estimate$upper[2],
    ligthart_results$pd$primary_r2_01$mr_results_corr@CIUpper
  ),
  pval = c(
    ligthart_results$pd$primary_r2_01$mr_results$ivw$estimate$pval,
    ligthart_results$pd$primary_r2_01$mr_results$egger$estimate$pval,
    ligthart_results$pd$primary_r2_01$mr_results$mr_median$estimate$pval,
    ligthart_results$pd$primary_r2_01$mr_results$mr_mode$estimate$pval,
    ligthart_results$pd$primary_r2_01$mr_results$presso$estimate$pval[2],
    ligthart_results$pd$primary_r2_01$mr_results_corr@Pvalue
  )
) %>% 
  mutate(
    across(c(est, lower, upper), ~ round(exp(.x), 3L)),
    outcome = "Parkinson's disease"
  )

# AAO ------------------------------------------------------------------
aao_res <- tibble(
  `MR method` = c(
      "IVW-RE", "MR-Egger", "Weighted median", "Weighted mode",
      "MR-PRESSO", "IVW-RE-Corr"
  ),
  est = c(
    ligthart_results$aao$primary_r2_01$mr_results$ivw$estimate$est,
    ligthart_results$aao$primary_r2_01$mr_results$egger$estimate$est,
    ligthart_results$aao$primary_r2_01$mr_results$mr_median$estimate$est,
    ligthart_results$aao$primary_r2_01$mr_results$mr_mode$estimate$est,
    ligthart_results$aao$primary_r2_01$mr_results$presso$estimate$est[2],
    ligthart_results$aao$primary_r2_01$mr_results_corr@Estimate
  ),
  lower = c(
    ligthart_results$aao$primary_r2_01$mr_results$ivw$estimate$lower,
    ligthart_results$aao$primary_r2_01$mr_results$egger$estimate$lower,
    ligthart_results$aao$primary_r2_01$mr_results$mr_median$estimate$lower,
    ligthart_results$aao$primary_r2_01$mr_results$mr_mode$estimate$lower,
    ligthart_results$aao$primary_r2_01$mr_results$presso$estimate$lower[2],
    ligthart_results$aao$primary_r2_01$mr_results_corr@CILower
  ),
  upper = c(
    ligthart_results$aao$primary_r2_01$mr_results$ivw$estimate$upper,
    ligthart_results$aao$primary_r2_01$mr_results$egger$estimate$upper,
    ligthart_results$aao$primary_r2_01$mr_results$mr_median$estimate$upper,
    ligthart_results$aao$primary_r2_01$mr_results$mr_mode$estimate$upper,
    ligthart_results$aao$primary_r2_01$mr_results$presso$estimate$upper[2],
    ligthart_results$aao$primary_r2_01$mr_results_corr@CIUpper
  ),
  pval = c(
    ligthart_results$aao$primary_r2_01$mr_results$ivw$estimate$pval,
    ligthart_results$aao$primary_r2_01$mr_results$egger$estimate$pval,
    ligthart_results$aao$primary_r2_01$mr_results$mr_median$estimate$pval,
    ligthart_results$aao$primary_r2_01$mr_results$mr_mode$estimate$pval,
    ligthart_results$aao$primary_r2_01$mr_results$presso$estimate$pval[2],
    ligthart_results$aao$primary_r2_01$mr_results_corr@Pvalue
  )
) %>% 
  mutate(outcome = "AAO")
```

```{r}
pd_res %>% 
  dplyr::select(-outcome) %>% 
  mutate(
    `OR (95% CI)` = glue::glue("{est} ({lower}; {upper})"),
    pval = if_else(
      pval < 0.001, "<0.001",
      as.character(round(pval, 3L))
    )
  ) %>% 
  dplyr::rename(`P-value` = pval) %>% 
  dplyr::select(`MR method`, `OR (95% CI)`, `P-value`) %>% 
  flextable() %>% 
  autofit() %>% 
  footnote(
    i = 1, j = 3,
    value = as_paragraph(
      "If MR-PRESSO results are set to NA, no outlier was identified and
      the final estimate equals the primary analysis estimate."
    ),
    ref_symbols = "a",
    part = "header", inline = TRUE
  ) %>% 
  set_caption(
    caption = "MR primary and secondary analysis results for CRP-PD with
    r2<0.1",
    autonum = autonum
  )
```
 
```{r}
aao_res %>% 
  dplyr::select(-outcome) %>% 
  mutate(across(c(est, lower, upper), ~ round(.x, 3L))) %>% 
  mutate(
    `Estimate (95% CI)` = glue::glue("{est} ({lower}; {upper})"),
    pval = if_else(
      pval < 0.001, "<0.001",
      as.character(round(pval, 3L))
    )
  ) %>% 
  dplyr::rename(`P-value` = pval) %>% 
  dplyr::select(`MR method`, `Estimate (95% CI)`, `P-value`) %>% 
  flextable() %>% 
  autofit() %>%
  footnote(
    i = 1, j = 3,
    value = as_paragraph(
      "If MR-PRESSO results are set to NA, no outlier was identified and
      the final estimate equals the primary analysis estimate."
    ),
    ref_symbols = "a",
    part = "header", inline = TRUE
  ) %>% 
  set_caption(
    caption = "MR primary and secondary analysis results for CRP-AAO with
    r2<0.1",
    autonum = autonum
  )
```

```{r}
pd_res <- tibble(
  `MR method` = c(
      "IVW-RE", "MR-Egger", "Weighted median", "Weighted mode", 
      "MR-PRESSO", "IVW-RE-Corr"
  ),
  est = c(
    ligthart_results$pd$sens_r2_01$mr_results$ivw$estimate$est,
    ligthart_results$pd$sens_r2_01$mr_results$egger$estimate$est,
    ligthart_results$pd$sens_r2_01$mr_results$mr_median$estimate$est,
    ligthart_results$pd$sens_r2_01$mr_results$mr_mode$estimate$est,
    ligthart_results$pd$sens_r2_01$mr_results$presso$estimate$est[2],
    ligthart_results$pd$sens_r2_01$mr_results_corr@Estimate
  ),
  lower = c(
    ligthart_results$pd$sens_r2_01$mr_results$ivw$estimate$lower,
    ligthart_results$pd$sens_r2_01$mr_results$egger$estimate$lower,
    ligthart_results$pd$sens_r2_01$mr_results$mr_median$estimate$lower,
    ligthart_results$pd$sens_r2_01$mr_results$mr_mode$estimate$lower,
    ligthart_results$pd$sens_r2_01$mr_results$presso$estimate$lower[2],
    ligthart_results$pd$sens_r2_01$mr_results_corr@CILower
  ),
  upper = c(
    ligthart_results$pd$sens_r2_01$mr_results$ivw$estimate$upper,
    ligthart_results$pd$sens_r2_01$mr_results$egger$estimate$upper,
    ligthart_results$pd$sens_r2_01$mr_results$mr_median$estimate$upper,
    ligthart_results$pd$sens_r2_01$mr_results$mr_mode$estimate$upper,
    ligthart_results$pd$sens_r2_01$mr_results$presso$estimate$upper[2],
    ligthart_results$pd$sens_r2_01$mr_results_corr@CIUpper
  ),
  pval = c(
    ligthart_results$pd$sens_r2_01$mr_results$ivw$estimate$pval,
    ligthart_results$pd$sens_r2_01$mr_results$egger$estimate$pval,
    ligthart_results$pd$sens_r2_01$mr_results$mr_median$estimate$pval,
    ligthart_results$pd$sens_r2_01$mr_results$mr_mode$estimate$pval,
    ligthart_results$pd$sens_r2_01$mr_results$presso$estimate$pval[2],
    ligthart_results$pd$sens_r2_01$mr_results_corr@Pvalue
  )
) %>% 
  mutate(
    across(c(est, lower, upper), ~ round(exp(.x), 3L)),
    outcome = "Parkinson's disease"
  )

# AAO ------------------------------------------------------------------
aao_res <- tibble(
  `MR method` = c(
      "IVW-RE", "MR-Egger", "Weighted median", "Weighted mode",
      "MR-PRESSO", "IVW-RE-Corr"
  ),
  est = c(
    ligthart_results$aao$sens_r2_01$mr_results$ivw$estimate$est,
    ligthart_results$aao$sens_r2_01$mr_results$egger$estimate$est,
    ligthart_results$aao$sens_r2_01$mr_results$mr_median$estimate$est,
    ligthart_results$aao$sens_r2_01$mr_results$mr_mode$estimate$est,
    ligthart_results$aao$sens_r2_01$mr_results$presso$estimate$est[2],
    ligthart_results$aao$sens_r2_01$mr_results_corr@Estimate
  ),
  lower = c(
    ligthart_results$aao$sens_r2_01$mr_results$ivw$estimate$lower,
    ligthart_results$aao$sens_r2_01$mr_results$egger$estimate$lower,
    ligthart_results$aao$sens_r2_01$mr_results$mr_median$estimate$lower,
    ligthart_results$aao$sens_r2_01$mr_results$mr_mode$estimate$lower,
    ligthart_results$aao$sens_r2_01$mr_results$presso$estimate$lower[2],
    ligthart_results$aao$sens_r2_01$mr_results_corr@CILower
  ),
  upper = c(
    ligthart_results$aao$sens_r2_01$mr_results$ivw$estimate$upper,
    ligthart_results$aao$sens_r2_01$mr_results$egger$estimate$upper,
    ligthart_results$aao$sens_r2_01$mr_results$mr_median$estimate$upper,
    ligthart_results$aao$sens_r2_01$mr_results$mr_mode$estimate$upper,
    ligthart_results$aao$sens_r2_01$mr_results$presso$estimate$upper[2],
    ligthart_results$aao$sens_r2_01$mr_results_corr@CIUpper
  ),
  pval = c(
    ligthart_results$aao$sens_r2_01$mr_results$ivw$estimate$pval,
    ligthart_results$aao$sens_r2_01$mr_results$egger$estimate$pval,
    ligthart_results$aao$sens_r2_01$mr_results$mr_median$estimate$pval,
    ligthart_results$aao$sens_r2_01$mr_results$mr_mode$estimate$pval,
    ligthart_results$aao$sens_r2_01$mr_results$presso$estimate$pval[2],
    ligthart_results$aao$sens_r2_01$mr_results_corr@Pvalue
  )
) %>% 
  mutate(outcome = "AAO")
```

```{r}
pd_res %>% 
  dplyr::select(-outcome) %>% 
  mutate(
    `OR (95% CI)` = glue::glue("{est} ({lower}; {upper})"),
    pval = if_else(
      pval < 0.001, "<0.001",
      as.character(round(pval, 3L))
    )
  ) %>% 
  dplyr::rename(`P-value` = pval) %>% 
  dplyr::select(`MR method`, `OR (95% CI)`, `P-value`) %>% 
  flextable() %>% 
  autofit() %>% 
  footnote(
    i = 1, j = 3,
    value = as_paragraph(
      "If MR-PRESSO results are set to NA, no outlier was identified and
      the final estimate equals the primary analysis estimate."
    ),
    ref_symbols = "a",
    part = "header", inline = TRUE
  ) %>% 
  set_caption(
    caption = "Sensitivity analysis results for CRP-PD with r2<0.1",
    autonum = autonum
  )
```
 
```{r}
aao_res %>% 
  dplyr::select(-outcome) %>% 
  mutate(across(c(est, lower, upper), ~ round(.x, 3L))) %>% 
  mutate(
    `Estimate (95% CI)` = glue::glue("{est} ({lower}; {upper})"),
    pval = if_else(
      pval < 0.001, "<0.001",
      as.character(round(pval, 3L))
    )
  ) %>% 
  dplyr::rename(`P-value` = pval) %>% 
  dplyr::select(`MR method`, `Estimate (95% CI)`, `P-value`) %>% 
  flextable() %>% 
  autofit() %>%
  footnote(
    i = 1, j = 3,
    value = as_paragraph(
      "If MR-PRESSO results are set to NA, no outlier was identified and
      the final estimate equals the primary analysis estimate."
    ),
    ref_symbols = "a",
    part = "header", inline = TRUE
  ) %>% 
  set_caption(
    caption = "Sensitivity analysis results for CRP-AAO with
    r2<0.1",
    autonum = autonum
  )
```

```{r}
# CCGC primary ---------------------------------------------------------
pd_res <- tibble(
  `MR method` = c("IVW-FE", "IVW-FE-Corr"),
  est = c(
    unique(ccgc_results$pd$primary_r2_01$mr_results$est),
    ccgc_results$pd$primary_r2_01$mr_results_corr@Estimate
  ),
  lower = c(
    unique(ccgc_results$pd$primary_r2_01$mr_results$lower),
    ccgc_results$pd$primary_r2_01$mr_results_corr@CILower
  ),
  upper = c(
    unique(ccgc_results$pd$primary_r2_01$mr_results$upper),
    ccgc_results$pd$primary_r2_01$mr_results_corr@CIUpper
  ),
  pval = c(
    unique(ccgc_results$pd$primary_r2_01$mr_results$pval),
    ccgc_results$pd$primary_r2_01$mr_results_corr@Pvalue
  )
) %>% 
  mutate(
    across(c(est, lower, upper), ~ round(exp(.x), 3L)),
    outcome = "Parkinson's disease"
  )

# AAO ------------------------------------------------------------------
aao_res <- tibble(
  `MR method` = c("IVW-FE", "IVW-FE-Corr"),
  est = c(
    unique(ccgc_results$aao$primary_r2_01$mr_results$est),
    ccgc_results$aao$primary_r2_01$mr_results_corr@Estimate
  ),
  lower = c(
    unique(ccgc_results$aao$primary_r2_01$mr_results$lower),
    ccgc_results$aao$primary_r2_01$mr_results_corr@CILower
  ),
  upper = c(
    unique(ccgc_results$aao$primary_r2_01$mr_results$upper),
    ccgc_results$aao$primary_r2_01$mr_results_corr@CIUpper
  ),
  pval = c(
    unique(ccgc_results$aao$primary_r2_01$mr_results$pval),
    ccgc_results$aao$primary_r2_01$mr_results_corr@Pvalue
  )
) %>% 
  mutate(outcome = "AAO")
```

```{r}
pd_res %>% 
  dplyr::select(-outcome) %>% 
  mutate(
    `OR (95% CI)` = glue::glue("{est} ({lower}; {upper})"),
    pval = if_else(
      pval < 0.001, "<0.001",
      as.character(round(pval, 3L))
    )
  ) %>% 
  dplyr::rename(`P-value` = pval) %>% 
  dplyr::select(`MR method`, `OR (95% CI)`, `P-value`) %>% 
  flextable() %>% 
  autofit() %>% 
  footnote(
    i = 1, j = 3,
    value = as_paragraph(
      "If MR-PRESSO results are set to NA, no outlier was identified and
      the final estimate equals the primary analysis estimate."
    ),
    ref_symbols = "a",
    part = "header", inline = TRUE
  ) %>% 
  set_caption(
    caption = "Primary MR analysis results for CRP-PD with r2<0.1",
    autonum = autonum
  )
```
 
```{r}
aao_res %>% 
  dplyr::select(-outcome) %>% 
  mutate(across(c(est, lower, upper), ~ round(.x, 3L))) %>% 
  mutate(
    `Estimate (95% CI)` = glue::glue("{est} ({lower}; {upper})"),
    pval = if_else(
      pval < 0.001, "<0.001",
      as.character(round(pval, 3L))
    )
  ) %>% 
  dplyr::rename(`P-value` = pval) %>% 
  dplyr::select(`MR method`, `Estimate (95% CI)`, `P-value`) %>% 
  flextable() %>% 
  autofit() %>%
  footnote(
    i = 1, j = 3,
    value = as_paragraph(
      "If MR-PRESSO results are set to NA, no outlier was identified and
      the final estimate equals the primary analysis estimate."
    ),
    ref_symbols = "a",
    part = "header", inline = TRUE
  ) %>% 
  set_caption(
    caption = "Primary MR analysis results for IL6-AAO with r2<0.1",
    autonum = autonum
  )
```
```


```{r}
# Ahluwalia primary ----------------------------------------------------
pd_res <- tibble(
  `MR method` = c(
    "IVW-RE", "MR-Egger", "Weighted median", "Weighted mode",
    "MR-PRESSO", "IVW-RE-Corr"
  ),
  est = c(
    ahluwalia_results$pd$primary_r2_01$mr_results$ivw$estimate$est,
    ahluwalia_results$pd$primary_r2_01$mr_results$egger$estimate$est,
    ahluwalia_results$pd$primary_r2_01$mr_results$mr_median$estimate$est,
    ahluwalia_results$pd$primary_r2_01$mr_results$mr_mode$estimate$est,
    ahluwalia_results$pd$primary_r2_01$mr_results$presso$estimate$est[2],
    ahluwalia_results$pd$primary_r2_01$mr_results_corr@Estimate
  ),
  lower = c(
    ahluwalia_results$pd$primary_r2_01$mr_results$ivw$estimate$lower,
    ahluwalia_results$pd$primary_r2_01$mr_results$egger$estimate$lower,
    ahluwalia_results$pd$primary_r2_01$mr_results$mr_median$estimate$lower,
    ahluwalia_results$pd$primary_r2_01$mr_results$mr_mode$estimate$lower,
    ahluwalia_results$pd$primary_r2_01$mr_results$presso$estimate$lower[2],
    ahluwalia_results$pd$primary_r2_01$mr_results_corr@CILower
  ),
  upper = c(
    ahluwalia_results$pd$primary_r2_01$mr_results$ivw$estimate$upper,
    ahluwalia_results$pd$primary_r2_01$mr_results$egger$estimate$upper,
    ahluwalia_results$pd$primary_r2_01$mr_results$mr_median$estimate$upper,
    ahluwalia_results$pd$primary_r2_01$mr_results$mr_mode$estimate$upper,
    ahluwalia_results$pd$primary_r2_01$mr_results$presso$estimate$upper[2],
    ahluwalia_results$pd$primary_r2_01$mr_results_corr@CIUpper
  ),
  pval = c(
    ahluwalia_results$pd$primary_r2_01$mr_results$ivw$estimate$pval,
    ahluwalia_results$pd$primary_r2_01$mr_results$egger$estimate$pval,
    ahluwalia_results$pd$primary_r2_01$mr_results$mr_median$estimate$pval,
    ahluwalia_results$pd$primary_r2_01$mr_results$mr_mode$estimate$pval,
    ahluwalia_results$pd$primary_r2_01$mr_results$presso$estimate$pval[2],
    ahluwalia_results$pd$primary_r2_01$mr_results_corr@Pvalue
  )
) %>% 
  mutate(
    across(c(est, lower, upper), ~ round(exp(.x), 3L)),
    outcome = "Parkinson's disease"
  )

# AAO ------------------------------------------------------------------
aao_res <- tibble(
  `MR method` = c(
    "IVW-RE", "MR-Egger", "Weighted median", "Weighted mode",
    "MR-PRESSO", "IVW-RE-Corr"
  ),
  est = c(
    ahluwalia_results$aao$primary_r2_01$mr_results$ivw$estimate$est,
    ahluwalia_results$aao$primary_r2_01$mr_results$egger$estimate$est,
    ahluwalia_results$aao$primary_r2_01$mr_results$mr_median$estimate$est,
    ahluwalia_results$aao$primary_r2_01$mr_results$mr_mode$estimate$est,
    ahluwalia_results$aao$primary_r2_01$mr_results$presso$estimate$est[2],
    ahluwalia_results$aao$primary_r2_01$mr_results_corr@Estimate
  ),
  lower = c(
    ahluwalia_results$aao$primary_r2_01$mr_results$ivw$estimate$lower,
    ahluwalia_results$aao$primary_r2_01$mr_results$egger$estimate$lower,
    ahluwalia_results$aao$primary_r2_01$mr_results$mr_median$estimate$lower,
    ahluwalia_results$aao$primary_r2_01$mr_results$mr_mode$estimate$lower,
    ahluwalia_results$aao$primary_r2_01$mr_results$presso$estimate$lower[2],
    ahluwalia_results$aao$primary_r2_01$mr_results_corr@CILower
  ),
  upper = c(
    ahluwalia_results$aao$primary_r2_01$mr_results$ivw$estimate$upper,
    ahluwalia_results$aao$primary_r2_01$mr_results$egger$estimate$upper,
    ahluwalia_results$aao$primary_r2_01$mr_results$mr_median$estimate$upper,
    ahluwalia_results$aao$primary_r2_01$mr_results$mr_mode$estimate$upper,
    ahluwalia_results$aao$primary_r2_01$mr_results$presso$estimate$upper[2],
    ahluwalia_results$aao$primary_r2_01$mr_results_corr@CIUpper
  ),
  pval = c(
    ahluwalia_results$aao$primary_r2_01$mr_results$ivw$estimate$pval,
    ahluwalia_results$aao$primary_r2_01$mr_results$egger$estimate$pval,
    ahluwalia_results$aao$primary_r2_01$mr_results$mr_median$estimate$pval,
    ahluwalia_results$aao$primary_r2_01$mr_results$mr_mode$estimate$pval,
    ahluwalia_results$aao$primary_r2_01$mr_results$presso$estimate$pval[2],
    ahluwalia_results$aao$primary_r2_01$mr_results_corr@Pvalue
  )
) %>% 
  mutate(outcome = "AAO")
```

```{r}
pd_res %>% 
  dplyr::select(-outcome) %>% 
  mutate(
    `OR (95% CI)` = glue::glue("{est} ({lower}; {upper})"),
    pval = if_else(
      pval < 0.001, "<0.001",
      as.character(round(pval, 3L))
    )
  ) %>% 
  dplyr::rename(`P-value` = pval) %>% 
  dplyr::select(`MR method`, `OR (95% CI)`, `P-value`) %>% 
  flextable() %>% 
  autofit() %>% 
  footnote(
    i = 1, j = 3,
    value = as_paragraph(
      "If MR-PRESSO results are set to NA, no outlier was identified and
      the final estimate equals the primary analysis estimate."
    ),
    ref_symbols = "a",
    part = "header", inline = TRUE
  ) %>% 
  set_caption(
    caption = "MR primary and secondary analysis results for IL6-PD with
    r2<0.1",
    autonum = autonum
  )
```
 
```{r}
aao_res %>% 
  dplyr::select(-outcome) %>% 
  mutate(across(c(est, lower, upper), ~ round(.x, 3L))) %>% 
  mutate(
    `Estimate (95% CI)` = glue::glue("{est} ({lower}; {upper})"),
    pval = if_else(
      pval < 0.001, "<0.001",
      as.character(round(pval, 3L))
    )
  ) %>% 
  dplyr::rename(`P-value` = pval) %>% 
  dplyr::select(`MR method`, `Estimate (95% CI)`, `P-value`) %>% 
  flextable() %>% 
  autofit() %>%
  footnote(
    i = 1, j = 3,
    value = as_paragraph(
      "If MR-PRESSO results are set to NA, no outlier was identified and
      the final estimate equals the primary analysis estimate."
    ),
    ref_symbols = "a",
    part = "header", inline = TRUE
  ) %>% 
  set_caption(
    caption = "MR primary and secondary analysis results for IL6-AAO with
    r2<0.1",
    autonum = autonum
  )
```

```{r}
# Ahluwalia sensitivity ------------------------------------------------
pd_res <- tibble(
  `MR method` = c("IVW-FE", "IVW-FE-Corr"),
  est = c(
    ahluwalia_results$pd$sens_r2_01$mr_results@Estimate,
    ahluwalia_results$pd$sens_r2_01$mr_results_corr@Estimate
  ),
  lower = c(
    ahluwalia_results$pd$sens_r2_01$mr_results@CILower,
    ahluwalia_results$pd$sens_r2_01$mr_results_corr@CILower
  ),
  upper = c(
    ahluwalia_results$pd$sens_r2_01$mr_results@CIUpper,
    ahluwalia_results$pd$sens_r2_01$mr_results_corr@CIUpper
  ),
  pval = c(
    ahluwalia_results$pd$sens_r2_01$mr_results@Pvalue,
    ahluwalia_results$pd$sens_r2_01$mr_results_corr@Pvalue
  )
) %>% 
  mutate(
    across(c(est, lower, upper), ~ round(exp(.x), 3L)),
    outcome = "Parkinson's disease"
  )

# AAO ------------------------------------------------------------------
aao_res <- tibble(
  `MR method` = c("IVW-FE", "IVW-FE-Corr"),
  est = c(
    ahluwalia_results$aao$sens_r2_01$mr_results@Estimate,
    ahluwalia_results$aao$sens_r2_01$mr_results_corr@Estimate
  ),
  lower = c(
    ahluwalia_results$aao$sens_r2_01$mr_results@CILower,
    ahluwalia_results$aao$sens_r2_01$mr_results_corr@CILower
  ),
  upper = c(
    ahluwalia_results$aao$sens_r2_01$mr_results@CIUpper,
    ahluwalia_results$aao$sens_r2_01$mr_results_corr@CIUpper
  ),
  pval = c(
    ahluwalia_results$aao$sens_r2_01$mr_results@Pvalue,
    ahluwalia_results$aao$sens_r2_01$mr_results_corr@Pvalue
  )
) %>% 
  mutate(outcome = "AAO")
```

```{r}
pd_res %>% 
  dplyr::select(-outcome) %>% 
  mutate(
    `OR (95% CI)` = glue::glue("{est} ({lower}; {upper})"),
    pval = if_else(
      pval < 0.001, "<0.001",
      as.character(round(pval, 3L))
    )
  ) %>% 
  dplyr::rename(`P-value` = pval) %>% 
  dplyr::select(`MR method`, `OR (95% CI)`, `P-value`) %>% 
  flextable() %>% 
  autofit() %>% 
  footnote(
    i = 1, j = 3,
    value = as_paragraph(
      "If MR-PRESSO results are set to NA, no outlier was identified and
      the final estimate equals the primary analysis estimate."
    ),
    ref_symbols = "a",
    part = "header", inline = TRUE
  ) %>% 
  set_caption(
    caption = "Sensitivity analysis results for IL6-PD with
    r2<0.1",
    autonum = autonum
  )
```
 
```{r}
aao_res %>% 
  dplyr::select(-outcome) %>% 
  mutate(across(c(est, lower, upper), ~ round(.x, 3L))) %>% 
  mutate(
    `Estimate (95% CI)` = glue::glue("{est} ({lower}; {upper})"),
    pval = if_else(
      pval < 0.001, "<0.001",
      as.character(round(pval, 3L))
    )
  ) %>% 
  dplyr::rename(`P-value` = pval) %>% 
  dplyr::select(`MR method`, `Estimate (95% CI)`, `P-value`) %>% 
  flextable() %>% 
  autofit() %>%
  footnote(
    i = 1, j = 3,
    value = as_paragraph(
      "If MR-PRESSO results are set to NA, no outlier was identified and
      the final estimate equals the primary analysis estimate."
    ),
    ref_symbols = "a",
    part = "header", inline = TRUE
  ) %>% 
  set_caption(
    caption = "Sensitivity analysis results for IL6-AAO with
    r2<0.1",
    autonum = autonum
  )
```

```{r}
# Folkersen primary ----------------------------------------------------
pd_res <- tibble(
  `MR method` = c(
    "IVW-RE", "MR-Egger", "Weighted median", "Weighted mode",
    "MR-PRESSO", "IVW-RE-Corr"
  ),
  est = c(
    folkersen_results$pd$primary_r2_01$mr_results$ivw$estimate$est,
    folkersen_results$pd$primary_r2_01$mr_results$egger$estimate$est,
    folkersen_results$pd$primary_r2_01$mr_results$mr_median$estimate$est,
    folkersen_results$pd$primary_r2_01$mr_results$mr_mode$estimate$est,
    folkersen_results$pd$primary_r2_01$mr_results$presso$estimate$est[2],
    folkersen_results$pd$primary_r2_01$mr_results_corr@Estimate
  ),
  lower = c(
    folkersen_results$pd$primary_r2_01$mr_results$ivw$estimate$lower,
    folkersen_results$pd$primary_r2_01$mr_results$egger$estimate$lower,
    folkersen_results$pd$primary_r2_01$mr_results$mr_median$estimate$lower,
    folkersen_results$pd$primary_r2_01$mr_results$mr_mode$estimate$lower,
    folkersen_results$pd$primary_r2_01$mr_results$presso$estimate$lower[2],
    folkersen_results$pd$primary_r2_01$mr_results_corr@CILower
  ),
  upper = c(
    folkersen_results$pd$primary_r2_01$mr_results$ivw$estimate$upper,
    folkersen_results$pd$primary_r2_01$mr_results$egger$estimate$upper,
    folkersen_results$pd$primary_r2_01$mr_results$mr_median$estimate$upper,
    folkersen_results$pd$primary_r2_01$mr_results$mr_mode$estimate$upper,
    folkersen_results$pd$primary_r2_01$mr_results$presso$estimate$upper[2],
    folkersen_results$pd$primary_r2_01$mr_results_corr@CIUpper
  ),
  pval = c(
    folkersen_results$pd$primary_r2_01$mr_results$ivw$estimate$pval,
    folkersen_results$pd$primary_r2_01$mr_results$egger$estimate$pval,
    folkersen_results$pd$primary_r2_01$mr_results$mr_median$estimate$pval,
    folkersen_results$pd$primary_r2_01$mr_results$mr_mode$estimate$pval,
    folkersen_results$pd$primary_r2_01$mr_results$presso$estimate$pval[2],
    folkersen_results$pd$primary_r2_01$mr_results_corr@Pvalue
  )
) %>% 
  mutate(
    across(c(est, lower, upper), ~ round(exp(.x), 3L)),
    outcome = "Parkinson's disease"
  )

# AAO ------------------------------------------------------------------
aao_res <- tibble(
  `MR method` = c(
    "IVW-RE", "MR-Egger", "Weighted median", "Weighted mode",
    "MR-PRESSO", "IVW-RE-Corr"
  ),
  est = c(
    folkersen_results$aao$primary_r2_01$mr_results$ivw$estimate$est,
    folkersen_results$aao$primary_r2_01$mr_results$egger$estimate$est,
    folkersen_results$aao$primary_r2_01$mr_results$mr_median$estimate$est,
    folkersen_results$aao$primary_r2_01$mr_results$mr_mode$estimate$est,
    folkersen_results$aao$primary_r2_01$mr_results$presso$estimate$est[2],
    folkersen_results$aao$primary_r2_01$mr_results_corr@Estimate
  ),
  lower = c(
    folkersen_results$aao$primary_r2_01$mr_results$ivw$estimate$lower,
    folkersen_results$aao$primary_r2_01$mr_results$egger$estimate$lower,
    folkersen_results$aao$primary_r2_01$mr_results$mr_median$estimate$lower,
    folkersen_results$aao$primary_r2_01$mr_results$mr_mode$estimate$lower,
    folkersen_results$aao$primary_r2_01$mr_results$presso$estimate$lower[2],
    folkersen_results$aao$primary_r2_01$mr_results_corr@CILower
  ),
  upper = c(
    folkersen_results$aao$primary_r2_01$mr_results$ivw$estimate$upper,
    folkersen_results$aao$primary_r2_01$mr_results$egger$estimate$upper,
    folkersen_results$aao$primary_r2_01$mr_results$mr_median$estimate$upper,
    folkersen_results$aao$primary_r2_01$mr_results$mr_mode$estimate$upper,
    folkersen_results$aao$primary_r2_01$mr_results$presso$estimate$upper[2],
    folkersen_results$aao$primary_r2_01$mr_results_corr@CIUpper
  ),
  pval = c(
    folkersen_results$aao$primary_r2_01$mr_results$ivw$estimate$pval,
    folkersen_results$aao$primary_r2_01$mr_results$egger$estimate$pval,
    folkersen_results$aao$primary_r2_01$mr_results$mr_median$estimate$pval,
    folkersen_results$aao$primary_r2_01$mr_results$mr_mode$estimate$pval,
    folkersen_results$aao$primary_r2_01$mr_results$presso$estimate$pval[2],
    folkersen_results$aao$primary_r2_01$mr_results_corr@Pvalue
  )
) %>% 
  mutate(outcome = "AAO")
```

```{r}
pd_res %>% 
  dplyr::select(-outcome) %>% 
  mutate(
    `OR (95% CI)` = glue::glue("{est} ({lower}; {upper})"),
    pval = if_else(
      pval < 0.001, "<0.001",
      as.character(round(pval, 3L))
    )
  ) %>% 
  dplyr::rename(`P-value` = pval) %>% 
  dplyr::select(`MR method`, `OR (95% CI)`, `P-value`) %>% 
  flextable() %>% 
  autofit() %>% 
  footnote(
    i = 1, j = 3,
    value = as_paragraph(
      "If MR-PRESSO results are set to NA, no outlier was identified and
      the final estimate equals the primary analysis estimate."
    ),
    ref_symbols = "a",
    part = "header", inline = TRUE
  ) %>% 
  set_caption(
    caption = "MR primary and secondary analysis results for IL6-PD with r2<0.1",
    autonum = autonum
  )
```
 
```{r}
aao_res %>% 
  dplyr::select(-outcome) %>% 
  mutate(across(c(est, lower, upper), ~ round(.x, 3L))) %>% 
  mutate(
    `Estimate (95% CI)` = glue::glue("{est} ({lower}; {upper})"),
    pval = if_else(
      pval < 0.001, "<0.001",
      as.character(round(pval, 3L))
    )
  ) %>% 
  dplyr::rename(`P-value` = pval) %>% 
  dplyr::select(`MR method`, `Estimate (95% CI)`, `P-value`) %>% 
  flextable() %>% 
  autofit() %>%
  footnote(
    i = 1, j = 3,
    value = as_paragraph(
      "If MR-PRESSO results are set to NA, no outlier was identified and
      the final estimate equals the primary analysis estimate."
    ),
    ref_symbols = "a",
    part = "header", inline = TRUE
  ) %>% 
  set_caption(
    caption = "MR primary and secondary analysis results for IL6-AAO 
    with r2<0.1",
    autonum = autonum
  )
```

```{r}
# PD estimates secondary -----------------------------------------------
pd_res <- tibble(
  `MR method` = c("IVW-FE", "IVW-FE-Corr"),
  est = c(
    folkersen_results$pd$sens_r2_01$mr_results@Estimate,
    folkersen_results$pd$sens_r2_01$mr_results_corr@Estimate
  ),
  lower = c(
    folkersen_results$pd$sens_r2_01$mr_results@CILower,
    folkersen_results$pd$sens_r2_01$mr_results_corr@CILower
  ),
  upper = c(
    folkersen_results$pd$sens_r2_01$mr_results@CIUpper,
    folkersen_results$pd$sens_r2_01$mr_results_corr@CIUpper
  ),
  pval = c(
    folkersen_results$pd$sens_r2_01$mr_results@Pvalue,
    folkersen_results$pd$sens_r2_01$mr_results_corr@Pvalue
  )
) %>% 
  mutate(
    across(c(est, lower, upper), ~ round(exp(.x), 3L)),
    outcome = "Parkinson's disease"
  )

# AAO ------------------------------------------------------------------
aao_res <- tibble(
  `MR method` = c("IVW-FE", "IVW-FE-Corr"),
  est = c(
    folkersen_results$aao$sens_r2_01$mr_results@Estimate,
    folkersen_results$aao$sens_r2_01$mr_results_corr@Estimate
  ),
  lower = c(
    folkersen_results$aao$sens_r2_01$mr_results@CILower,
    folkersen_results$aao$sens_r2_01$mr_results_corr@CILower
  ),
  upper = c(
    folkersen_results$aao$sens_r2_01$mr_results@CIUpper,
    folkersen_results$aao$sens_r2_01$mr_results_corr@CIUpper
  ),
  pval = c(
    folkersen_results$aao$sens_r2_01$mr_results@Pvalue,
    folkersen_results$aao$sens_r2_01$mr_results_corr@Pvalue
  )
) %>% 
  mutate(outcome = "AAO")
```

```{r}
pd_res %>% 
  dplyr::select(-outcome) %>% 
  mutate(
    `OR (95% CI)` = glue::glue("{est} ({lower}; {upper})"),
    pval = if_else(
      pval < 0.001, "<0.001",
      as.character(round(pval, 3L))
    )
  ) %>% 
  dplyr::rename(`P-value` = pval) %>% 
  dplyr::select(`MR method`, `OR (95% CI)`, `P-value`) %>% 
  flextable() %>% 
  autofit() %>% 
  footnote(
    i = 1, j = 3,
    value = as_paragraph(
      "If MR-PRESSO results are set to NA, no outlier was identified and
      the final estimate equals the primary analysis estimate."
    ),
    ref_symbols = "a",
    part = "header", inline = TRUE
  ) %>% 
  set_caption(
    caption = "Sensitivity analysis results for IL6-PD with r2<0.1",
    autonum = autonum
  )
```
 
```{r}
aao_res %>% 
  dplyr::select(-outcome) %>% 
  mutate(across(c(est, lower, upper), ~ round(.x, 3L))) %>% 
  mutate(
    `Estimate (95% CI)` = glue::glue("{est} ({lower}; {upper})"),
    pval = if_else(
      pval < 0.001, "<0.001",
      as.character(round(pval, 3L))
    )
  ) %>% 
  dplyr::rename(`P-value` = pval) %>% 
  dplyr::select(`MR method`, `Estimate (95% CI)`, `P-value`) %>% 
  flextable() %>% 
  autofit() %>%
  footnote(
    i = 1, j = 3,
    value = as_paragraph(
      "If MR-PRESSO results are set to NA, no outlier was identified and
      the final estimate equals the primary analysis estimate."
    ),
    ref_symbols = "a",
    part = "header", inline = TRUE
  ) %>% 
  set_caption(
    caption = "Sensitivity analysis results for IL6-AAO with r2<0.1",
    autonum = autonum
  )
```

```{r}
# IL-1ra primary -------------------------------------------------------
pd_res <- tibble(
  `MR method` = c(
      "IVW-RE", "MR-Egger", "Weighted median", "Weighted mode",
      "MR-PRESSO", "IVW-RE-Corr"
  ),
  est = c(
    il1ra_results$pd$primary_r2_01$mr_results$ivw$estimate$est,
    il1ra_results$pd$primary_r2_01$mr_results$egger$estimate$est,
    il1ra_results$pd$primary_r2_01$mr_results$mr_median$estimate$est,
    il1ra_results$pd$primary_r2_01$mr_results$mr_mode$estimate$est,
    il1ra_results$pd$primary_r2_01$mr_results$presso$estimate$est[2],
    il1ra_results$pd$primary_r2_01$mr_results_corr@Estimate
  ),
  lower = c(
    il1ra_results$pd$primary_r2_01$mr_results$ivw$estimate$lower,
    il1ra_results$pd$primary_r2_01$mr_results$egger$estimate$lower,
    il1ra_results$pd$primary_r2_01$mr_results$mr_median$estimate$lower,
    il1ra_results$pd$primary_r2_01$mr_results$mr_mode$estimate$lower,
    il1ra_results$pd$primary_r2_01$mr_results$presso$estimate$lower[2],
    il1ra_results$pd$primary_r2_01$mr_results_corr@CILower
  ),
  upper = c(
    il1ra_results$pd$primary_r2_01$mr_results$ivw$estimate$upper,
    il1ra_results$pd$primary_r2_01$mr_results$egger$estimate$upper,
    il1ra_results$pd$primary_r2_01$mr_results$mr_median$estimate$upper,
    il1ra_results$pd$primary_r2_01$mr_results$mr_mode$estimate$upper,
    il1ra_results$pd$primary_r2_01$mr_results$presso$estimate$upper[2],
    il1ra_results$pd$primary_r2_01$mr_results_corr@CIUpper
  ),
  pval = c(
    il1ra_results$pd$primary_r2_01$mr_results$ivw$estimate$pval,
    il1ra_results$pd$primary_r2_01$mr_results$egger$estimate$pval,
    il1ra_results$pd$primary_r2_01$mr_results$mr_median$estimate$pval,
    il1ra_results$pd$primary_r2_01$mr_results$mr_mode$estimate$pval,
    il1ra_results$pd$primary_r2_01$mr_results$presso$estimate$pval[2],
    il1ra_results$pd$primary_r2_01$mr_results_corr@Pvalue
  )
) %>% 
  mutate(
    across(c(est, lower, upper), ~ round(exp(.x), 3L)),
    outcome = "Parkinson's disease"
  )

# AAO ------------------------------------------------------------------
aao_res <- tibble(
  `MR method` = c(
      "IVW-RE", "MR-Egger", "Weighted median", "Weighted mode",
      "MR-PRESSO", "IVW-RE-Corr"
  ),
  est = c(
    il1ra_results$aao$primary_r2_01$mr_results$ivw$estimate$est,
    il1ra_results$aao$primary_r2_01$mr_results$egger$estimate$est,
    il1ra_results$aao$primary_r2_01$mr_results$mr_median$estimate$est,
    il1ra_results$aao$primary_r2_01$mr_results$mr_mode$estimate$est,
    il1ra_results$aao$primary_r2_01$mr_results$presso$estimate$est[2],
    il1ra_results$aao$primary_r2_01$mr_results_corr@Estimate
  ),
  lower = c(
    il1ra_results$aao$primary_r2_01$mr_results$ivw$estimate$lower,
    il1ra_results$aao$primary_r2_01$mr_results$egger$estimate$lower,
    il1ra_results$aao$primary_r2_01$mr_results$mr_median$estimate$lower,
    il1ra_results$aao$primary_r2_01$mr_results$mr_mode$estimate$lower,
    il1ra_results$aao$primary_r2_01$mr_results$presso$estimate$lower[2],
    il1ra_results$aao$primary_r2_01$mr_results_corr@CILower
  ),
  upper = c(
    il1ra_results$aao$primary_r2_01$mr_results$ivw$estimate$upper,
    il1ra_results$aao$primary_r2_01$mr_results$egger$estimate$upper,
    il1ra_results$aao$primary_r2_01$mr_results$mr_median$estimate$upper,
    il1ra_results$aao$primary_r2_01$mr_results$mr_mode$estimate$upper,
    il1ra_results$aao$primary_r2_01$mr_results$presso$estimate$upper[2],
    il1ra_results$aao$primary_r2_01$mr_results_corr@CIUpper
  ),
  pval = c(
    il1ra_results$aao$primary_r2_01$mr_results$ivw$estimate$pval,
    il1ra_results$aao$primary_r2_01$mr_results$egger$estimate$pval,
    il1ra_results$aao$primary_r2_01$mr_results$mr_median$estimate$pval,
    il1ra_results$aao$primary_r2_01$mr_results$mr_mode$estimate$pval,
    il1ra_results$aao$primary_r2_01$mr_results$presso$estimate$pval[2],
    il1ra_results$aao$primary_r2_01$mr_results_corr@Pvalue
  )
) %>% 
  mutate(outcome = "AAO")
```

```{r}
pd_res %>% 
  dplyr::select(-outcome) %>% 
  mutate(
    `OR (95% CI)` = glue::glue("{est} ({lower}; {upper})"),
    pval = if_else(
      pval < 0.001, "<0.001",
      as.character(round(pval, 3L))
    )
  ) %>% 
  dplyr::rename(`P-value` = pval) %>% 
  dplyr::select(`MR method`, `OR (95% CI)`, `P-value`) %>% 
  flextable() %>% 
  autofit() %>% 
  footnote(
    i = 1, j = 3,
    value = as_paragraph(
      "If MR-PRESSO results are set to NA, no outlier was identified and
      the final estimate equals the primary analysis estimate."
    ),
    ref_symbols = "a",
    part = "header", inline = TRUE
  ) %>% 
  set_caption(
    caption = "MR primary and secondary analysis results for IL1ra-PD
    with r2<0.1",
    autonum = autonum
  )
```
 
```{r}
aao_res %>% 
  dplyr::select(-outcome) %>% 
  mutate(across(c(est, lower, upper), ~ round(.x, 3L))) %>% 
  mutate(
    `Estimate (95% CI)` = glue::glue("{est} ({lower}; {upper})"),
    pval = if_else(
      pval < 0.001, "<0.001",
      as.character(round(pval, 3L))
    )
  ) %>% 
  dplyr::rename(`P-value` = pval) %>% 
  dplyr::select(`MR method`, `Estimate (95% CI)`, `P-value`) %>% 
  flextable() %>% 
  autofit() %>%
  footnote(
    i = 1, j = 3,
    value = as_paragraph(
      "If MR-PRESSO results are set to NA, no outlier was identified and
      the final estimate equals the primary analysis estimate."
    ),
    ref_symbols = "a",
    part = "header", inline = TRUE
  ) %>% 
  set_caption(
    caption = "MR primary and secondary analysis results for IL1ra-AAO
    with r2<0.1",
    autonum = autonum
  )
```

```{r}
# IL-1ra sensitivity ---------------------------------------------------
pd_res <- tibble(
  `MR method` = c(
      "IVW-RE", "MR-Egger", "Weighted median", "Weighted mode",
      "MR-PRESSO", "IVW-RE-Corr"
  ),
  est = c(
    il1ra_results$pd$sens_r2_01$mr_results$ivw$estimate$est,
    il1ra_results$pd$sens_r2_01$mr_results$egger$estimate$est,
    il1ra_results$pd$sens_r2_01$mr_results$mr_median$estimate$est,
    il1ra_results$pd$sens_r2_01$mr_results$mr_mode$estimate$est,
    il1ra_results$pd$sens_r2_01$mr_results$presso$estimate$est[2],
    il1ra_results$pd$sens_r2_01$mr_results_corr@Estimate
  ),
  lower = c(
    il1ra_results$pd$sens_r2_01$mr_results$ivw$estimate$lower,
    il1ra_results$pd$sens_r2_01$mr_results$egger$estimate$lower,
    il1ra_results$pd$sens_r2_01$mr_results$mr_median$estimate$lower,
    il1ra_results$pd$sens_r2_01$mr_results$mr_mode$estimate$lower,
    il1ra_results$pd$sens_r2_01$mr_results$presso$estimate$lower[2],
    il1ra_results$pd$sens_r2_01$mr_results_corr@CILower
  ),
  upper = c(
    il1ra_results$pd$sens_r2_01$mr_results$ivw$estimate$upper,
    il1ra_results$pd$sens_r2_01$mr_results$egger$estimate$upper,
    il1ra_results$pd$sens_r2_01$mr_results$mr_median$estimate$upper,
    il1ra_results$pd$sens_r2_01$mr_results$mr_mode$estimate$upper,
    il1ra_results$pd$sens_r2_01$mr_results$presso$estimate$upper[2],
    il1ra_results$pd$sens_r2_01$mr_results_corr@CIUpper
  ),
  pval = c(
    il1ra_results$pd$sens_r2_01$mr_results$ivw$estimate$pval,
    il1ra_results$pd$sens_r2_01$mr_results$egger$estimate$pval,
    il1ra_results$pd$sens_r2_01$mr_results$mr_median$estimate$pval,
    il1ra_results$pd$sens_r2_01$mr_results$mr_mode$estimate$pval,
    il1ra_results$pd$sens_r2_01$mr_results$presso$estimate$pval[2],
    il1ra_results$pd$sens_r2_01$mr_results_corr@Pvalue
  )
) %>% 
  mutate(
    across(c(est, lower, upper), ~ round(exp(.x), 3L)),
    outcome = "Parkinson's disease"
  )

# AAO ------------------------------------------------------------------
aao_res <- tibble(
  `MR method` = c(
      "IVW-RE", "MR-Egger", "Weighted median", "Weighted mode",
      "MR-PRESSO", "IVW-RE-Corr"
  ),
  est = c(
    il1ra_results$aao$sens_r2_01$mr_results$ivw$estimate$est,
    il1ra_results$aao$sens_r2_01$mr_results$egger$estimate$est,
    il1ra_results$aao$sens_r2_01$mr_results$mr_median$estimate$est,
    il1ra_results$aao$sens_r2_01$mr_results$mr_mode$estimate$est,
    il1ra_results$aao$sens_r2_01$mr_results$presso$estimate$est[2],
    il1ra_results$aao$sens_r2_01$mr_results_corr@Estimate
  ),
  lower = c(
    il1ra_results$aao$sens_r2_01$mr_results$ivw$estimate$lower,
    il1ra_results$aao$sens_r2_01$mr_results$egger$estimate$lower,
    il1ra_results$aao$sens_r2_01$mr_results$mr_median$estimate$lower,
    il1ra_results$aao$sens_r2_01$mr_results$mr_mode$estimate$lower,
    il1ra_results$aao$sens_r2_01$mr_results$presso$estimate$lower[2],
    il1ra_results$aao$sens_r2_01$mr_results_corr@CILower
  ),
  upper = c(
    il1ra_results$aao$sens_r2_01$mr_results$ivw$estimate$upper,
    il1ra_results$aao$sens_r2_01$mr_results$egger$estimate$upper,
    il1ra_results$aao$sens_r2_01$mr_results$mr_median$estimate$upper,
    il1ra_results$aao$sens_r2_01$mr_results$mr_mode$estimate$upper,
    il1ra_results$aao$sens_r2_01$mr_results$presso$estimate$upper[2],
    il1ra_results$aao$sens_r2_01$mr_results_corr@CIUpper
  ),
  pval = c(
    il1ra_results$aao$sens_r2_01$mr_results$ivw$estimate$pval,
    il1ra_results$aao$sens_r2_01$mr_results$egger$estimate$pval,
    il1ra_results$aao$sens_r2_01$mr_results$mr_median$estimate$pval,
    il1ra_results$aao$sens_r2_01$mr_results$mr_mode$estimate$pval,
    il1ra_results$aao$sens_r2_01$mr_results$presso$estimate$pval[2],
    il1ra_results$aao$sens_r2_01$mr_results_corr@Pvalue
  )
) %>% 
  mutate(outcome = "AAO")
```

```{r}
pd_res %>% 
  dplyr::select(-outcome) %>% 
  mutate(
    `OR (95% CI)` = glue::glue("{est} ({lower}; {upper})"),
    pval = if_else(
      pval < 0.001, "<0.001",
      as.character(round(pval, 3L))
    )
  ) %>% 
  dplyr::rename(`P-value` = pval) %>% 
  dplyr::select(`MR method`, `OR (95% CI)`, `P-value`) %>% 
  flextable() %>% 
  autofit() %>% 
  footnote(
    i = 1, j = 3,
    value = as_paragraph(
      "If MR-PRESSO results are set to NA, no outlier was identified and
      the final estimate equals the primary analysis estimate."
    ),
    ref_symbols = "a",
    part = "header", inline = TRUE
  ) %>% 
  set_caption(
    caption = "MR Sensitivity analysis results for IL1RA-PD with r2<0.1",
    autonum = autonum
  )
```
 
```{r}
aao_res %>% 
  dplyr::select(-outcome) %>% 
  mutate(across(c(est, lower, upper), ~ round(.x, 3L))) %>% 
  mutate(
    `Estimate (95% CI)` = glue::glue("{est} ({lower}; {upper})"),
    pval = if_else(
      pval < 0.001, "<0.001",
      as.character(round(pval, 3L))
    )
  ) %>% 
  dplyr::rename(`P-value` = pval) %>% 
  dplyr::select(`MR method`, `Estimate (95% CI)`, `P-value`) %>% 
  flextable() %>% 
  autofit() %>%
  footnote(
    i = 1, j = 3,
    value = as_paragraph(
      "If MR-PRESSO results are set to NA, no outlier was identified and
      the final estimate equals the primary analysis estimate."
    ),
    ref_symbols = "a",
    part = "header", inline = TRUE
  ) %>% 
  set_caption(
    caption = "MR sensitivity analysis results for IL1RA-AAO with r2<0.1",
    autonum = autonum
  )
```

### Biological pleiotropy lookup

```{r}
ligthart_results$pd$sens_r2_0001$pleiotropic_snps$lookup %>% 
  dplyr::select(
    snp, hg19_coordinates, trait, trait_macro, study, beta, se, p 
  ) %>% 
  flextable() %>%
  autofit() %>% 
  set_caption(
    caption = "Pleiotropy lookup for CRP-PD",
    autonum = autonum
  )
```

```{r}
bind_rows(
  ahluwalia_results$pd$sens_r2_0001s$pleiotropic_snps$lookup,
  folkersen_results$pd$sens_r2_0001$pleiotropic_snps
) %>% 
  dplyr::select(
    snp, hg19_coordinates, trait, trait_macro, study, beta, se, p 
  ) %>% 
  flextable() %>%
  autofit() %>% 
  set_caption(
    caption = "Pleiotropy lookup for IL6-PD",
    autonum = autonum
  )
```

```{r}
tnf_results$pd$sens$pleiotropic_snps$lookup %>% 
  dplyr::select(
    snp, hg19_coordinates, trait, trait_macro, study, beta, se, p 
  ) %>% 
  flextable() %>%
  autofit() %>% 
  set_caption(
    caption = "Pleiotropy lookup for TNF-alpha-PD",
    autonum = autonum
  )
```
